---
title: "Fianl project code for extra credit"
author: "Justin Kowalski"
date: "2024-04-30"
output: html_document
---
Packages
```{r}
require(tidyverse)
require(sf)
require(tigris)
require(geodata)
require(terra)
require(colorspace)
require(tidyterra)
require(ggnewscale)
require(cowplot)
require(FedData)
require(ggspatial)
require(adehabitatLT)
require(ggplot2)
require(adehabitatHR)
require(dplyr)
require(sp)
```


The first chunk of code is for making my map of Alabama. The second panel in the figure in my paper that has the receiver locations was created in Arcgis Pro. 
```{r}
claibornesf <- st_read("/vsicurl/https://github.com/14jukowalski/SpatialEcology/raw/main/Lab_2/Claiborne_shapefile/Claiborne.shp")
plot(st_geometry(claibornesf))

claiborne = st_bbox(claibornesf)
claiborne

claiborne = claiborne + c(-20000, -20000, 20000, 20000)
claiborne

claiborne = st_as_sfc(claiborne)
plot(claiborne)

Alabama = states() %>% 
  filter(NAME=='Alabama')

plot(st_geometry(Alabama))

st_crs(Alabama)$proj4string

Alabama = st_transform(Alabama, st_crs(claibornesf))

plot(st_geometry(Alabama))
plot(claiborne, col='red', add=T)

zoomedOut = ggplot()+
  geom_sf(data = Alabama)+
  geom_sf(data = claiborne, fill=NA, color='red')+
  annotation_scale(location="br")+
  annotation_north_arrow(location = "tr")
zoomedOut

zoomedOut = zoomedOut +
  theme_bw()+ #Gets rid of most of the colors
  theme(panel.grid=element_blank(), #Removes the gridlines
        axis.text=element_blank(), #Removes the axis text
        axis.ticks=element_blank(), #Removes the axis tick marks
        panel.border=element_blank()) #Removes the frame around the graph
zoomedOut
```

First to make sure the simulatons ran correctly I ran one replicate of each simulation and plotted what each simulation looked like. Note: when I run the plot in R markdown I get an error that the figure margins are too large, but if I run the code in a R script with the large plot window it runs correctly.
```{r}
set.seed(6)
a <- simm.mou(1:25, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0036, 0.0036)),
                       burst="Variable attraction")

b <- simm.mou(1:50, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0036, 0.0036)),
              burst="Variable attraction")

c <- simm.mou(1:75, b=c(-87.5526154,31.61337824),sigma = diag(c(0.0036, 0.0036)),
              burst="Variable attraction")

d <- simm.mou(1:100, b=c(-87.5526154,31.61337824),sigma = diag(c(0.0036, 0.0036)),
              burst="Variable attraction")

e <- simm.mou(1:150, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0036, 0.0036)),
              burst="Variable attraction")

f <- simm.mou(1:200, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0036, 0.0036)),
              burst="Variable attraction")

g <- simm.mou(1:250, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0036, 0.0036)),
              burst="Variable attraction")

h <- simm.mou(1:300, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0036, 0.0036)),
              burst="Variable attraction")

#plot of the simulations
par(mfrow=c(3,3))
aplot = plot(a, cex.main = 1.5, cex.lab = 1.5, cex.axis = 1.5, main = "25 points", ylab = "Latitude", xlab = "", addpoints = FALSE, perani = FALSE)
bplot = plot(b, cex.main = 1.5, cex.lab = 1.5, cex.axis = 1.5, main = "50 points", ylab = "", xlab = "",addpoints = FALSE, perani = FALSE)
cplot = plot(c, cex.main = 1.5, cex.lab = 1.5, cex.axis = 1.5, main = "75 points", ylab = "", xlab = "",addpoints = FALSE, perani = FALSE)
dplot = plot(d, cex.main = 1.5, cex.lab = 1.5, cex.axis = 1.5, main = "100 points", ylab = "Latitude", xlab = "",addpoints = FALSE, perani = FALSE)
eplot = plot(e, cex.main = 1.5, cex.lab = 1.5, cex.axis = 1.5, main = "150 points", ylab = "", xlab = "Longitude", addpoints = FALSE, perani = FALSE)
fplot = plot(f, cex.main = 1.5, cex.lab = 1.5, cex.axis = 1.5, main = "200 points", ylab = "", xlab = "Longitude", addpoints = FALSE, perani = FALSE)
gplot = plot(g, cex.main = 1.5, cex.lab = 1.5, cex.axis = 1.5, main = "250 points", ylab = "Latitude", xlab = "Longitude", addpoints = FALSE, perani = FALSE)
hplot = plot(h, cex.main = 1.5, cex.lab = 1.5, cex.axis = 1.5, main = "300 points", ylab = "Latitude", xlab = "Longitude", addpoints = FALSE, perani = FALSE)

```

Next I ran one replication of each simulation (a-h) for each home range estimation method and plotted it to make sure the code worked and was correct.

Start with minimum convext polygon
```{r}
#mcp
#a
x = a[[1]][["x"]]
y = a[[1]][["y"]]

adf = data.frame(x,y)
adf = st_as_sf(x=adf, coords=c('x', 'y'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs") #Transforming simulated points to shapefile
adf = st_transform(adf, crs = st_crs(6345)) ##Transforming NAD83 (2011) to UTM zone 16
adf = adf %>% 
  mutate(id = 1)
aSp = as(adf, 'Spatial')
amcp95 = mcp(aSp, percent = 95, unin='m', unout='km2') 
amcp95


#b
bx = b[[1]][["x"]]
by = b[[1]][["y"]]

bdf = data.frame(bx,by)
bdf = st_as_sf(x=bdf, coords=c('bx', 'by'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
bdf = st_transform(bdf, crs = st_crs(6345))
bdf = bdf %>% 
  mutate(id = 1)
bSp = as(bdf, 'Spatial')
bmcp95 = mcp(bSp, percent = 95, unin='m', unout='km2')
bmcp95

#c
cx = c[[1]][["x"]]
cy = c[[1]][["y"]]

cdf = data.frame(cx,cy)
cdf = st_as_sf(x=cdf, coords=c('cx', 'cy'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
cdf = st_transform(cdf, crs = st_crs(6345))
cdf = cdf %>% 
  mutate(id = 1)
cSp = as(cdf, 'Spatial')
cmcp95 = mcp(cSp, percent = 95, unin='m', unout='km2')
cmcp95

#d
dx = d[[1]][["x"]]
dy = d[[1]][["y"]]

ddf = data.frame(dx,dy)
ddf = st_as_sf(x=ddf, coords=c('dx', 'dy'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
ddf = st_transform(ddf, crs = st_crs(6345))
ddf = ddf %>% 
  mutate(id = 1)
dSp = as(ddf, 'Spatial')
dmcp95 = mcp(dSp, percent = 95, unin='m', unout='km2')
dmcp95

#e
ex = e[[1]][["x"]]
ey = e[[1]][["y"]]

edf = data.frame(ex,ey)
edf = st_as_sf(x=edf, coords=c('ex', 'ey'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
edf = st_transform(edf, crs = st_crs(6345))
edf = edf %>% 
  mutate(id = 1)
eSp = as(edf, 'Spatial')
emcp95 = mcp(eSp, percent = 95, unin='m', unout='km2')
emcp95

#f
fx = f[[1]][["x"]]
fy = f[[1]][["y"]]

fdf = data.frame(fx,fy)
fdf = st_as_sf(x=fdf, coords=c('fx', 'fy'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
fdf = st_transform(fdf, crs = st_crs(6345))
fdf = fdf %>% 
  mutate(id = 1)
fSp = as(fdf, 'Spatial')
fmcp95 = mcp(fSp, percent = 95, unin='m', unout='km2')
fmcp95

#g
gx = g[[1]][["x"]]
gy = g[[1]][["y"]]

gdf = data.frame(gx,gy)
gdf = st_as_sf(x=gdf, coords=c('gx', 'gy'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
gdf = st_transform(gdf, crs = st_crs(6345))
gdf = gdf %>% 
  mutate(id = 1)
gSp = as(gdf, 'Spatial')
gmcp95 = mcp(gSp, percent = 95, unin='m', unout='km2')
gmcp95

#h
hx = h[[1]][["x"]]
hy = h[[1]][["y"]]

hdf = data.frame(hx,hy)
hdf = st_as_sf(x=hdf, coords=c('hx', 'hy'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs") 
hdf = st_transform(hdf, crs = st_crs(6345))
hdf = hdf %>% 
  mutate(id = 1)
hSp = as(hdf, 'Spatial')
hmcp95 = mcp(hSp, percent = 95, unin='m', unout='km2')
hmcp95

##plot of mcp
mcps = c(amcp95$area, bmcp95$area, cmcp95$area, dmcp95$area, emcp95$area, fmcp95$area, gmcp95$area, hmcp95$area)
xvals = c(25, 50, 75, 100, 150, 200, 250, 300)
plot(xvals, mcps)
```

Kernel Density
```{r}
#kernel density
#a
akernelHrefEpa = kernelUD(aSp, h='href', kern='epa')
kernel.area(akernelHrefEpa, unin = "m", unout = "km2")

#b
bkernelHrefEpa = kernelUD(bSp, h='href', kern='epa')
kernel.area(bkernelHrefEpa, unin = "m", unout = "km2")

#c
ckernelHrefEpa = kernelUD(cSp, h='href', kern='epa')
kernel.area(ckernelHrefEpa, unin = "m", unout = "km2")

#d
dkernelHrefEpa = kernelUD(dSp, h='href', kern='epa')
kernel.area(dkernelHrefEpa, unin = "m", unout = "km2")

#e
ekernelHrefEpa = kernelUD(eSp, h='href', kern='epa')
kernel.area(ekernelHrefEpa, unin = "m", unout = "km2")

#f
fkernelHrefEpa = kernelUD(fSp, h='href', kern='epa')
kernel.area(fkernelHrefEpa, unin = "m", unout = "km2")

#g
gkernelHrefEpa = kernelUD(gSp, h='href', kern='epa')
kernel.area(gkernelHrefEpa, unin = "m", unout = "km2")


#h
hkernelHrefEpa = kernelUD(hSp, h='href', kern='epa')
kernel.area(hkernelHrefEpa, unin = "m", unout = "km2")


#Kernel plot
ke = c(2.44, 3.36, 2.68, 2.91, 3.43, 3.41, 3.95, 3.57)
plot(xvals, ke)

```

And finally local convex hull
```{r}
#a-LoCoH
#a
aaInit = round(max(dist(coordinates(aSp))),0)
aaSearch = seq(aaInit, 2*aaInit, by=100)
alocohArange = LoCoH.a.area(SpatialPoints(coordinates(aSp)), arange=aaSearch)
alocohA = LoCoH.a(SpatialPoints(coordinates(aSp)), a=aaSearch[5], unin = "m", unout = "km2")
alocohASf = st_as_sf(alocohA)
alocohA96Sf = alocohASf[23,]
alocohA96Sf

#b
baInit = round(max(dist(coordinates(bSp))),0)
baSearch = seq(baInit, 2*baInit, by=100)
blocohArange = LoCoH.a.area(SpatialPoints(coordinates(bSp)), arange=baSearch)
blocohA = LoCoH.a(SpatialPoints(coordinates(bSp)), a=baSearch[14], unin = "m", unout = "km2")
blocohASf = st_as_sf(blocohA)
blocohA94Sf = blocohASf[44,]
blocohA94Sf

#c
caInit = round(max(dist(coordinates(cSp))),0)
caSearch = seq(caInit, 2*caInit, by=100)
clocohArange = LoCoH.a.area(SpatialPoints(coordinates(cSp)), arange=caSearch)
clocohA = LoCoH.a(SpatialPoints(coordinates(cSp)), a=caSearch[16], unin = "m", unout = "km2")
clocohASf = st_as_sf(clocohA)
clocohA95Sf = clocohASf[63,]
clocohA95Sf

#d
daInit = round(max(dist(coordinates(dSp))),0)
daSearch = seq(daInit, 2*daInit, by=100)
dlocohArange = LoCoH.a.area(SpatialPoints(coordinates(dSp)), arange=daSearch)
dlocohA = LoCoH.a(SpatialPoints(coordinates(dSp)), a=daSearch[11], unin = "m", unout = "km2")
dlocohASf = st_as_sf(dlocohA)
dlocohA96Sf = dlocohASf[79,]
dlocohA96Sf

#e
eaInit = round(max(dist(coordinates(eSp))),0)
eaSearch = seq(eaInit, 2*eaInit, by=100)
elocohArange = LoCoH.a.area(SpatialPoints(coordinates(eSp)), arange=eaSearch)
elocohA = LoCoH.a(SpatialPoints(coordinates(eSp)), a=eaSearch[23], unin = "m", unout = "km2")
elocohASf = st_as_sf(elocohA)
elocohA95Sf = elocohASf[127,]
elocohA95Sf

#f
faInit = round(max(dist(coordinates(fSp))),0)
faSearch = seq(faInit, 2*faInit, by=100)
flocohArange = LoCoH.a.area(SpatialPoints(coordinates(fSp)), arange=faSearch)
flocohA = LoCoH.a(SpatialPoints(coordinates(fSp)), a=faSearch[19], unin = "m", unout = "km2")
flocohASf = st_as_sf(flocohA)
flocohA95Sf = flocohASf[149,]
flocohA95Sf

#g
gaInit = round(max(dist(coordinates(gSp))),0)
gaSearch = seq(gaInit, 2*gaInit, by=100)
glocohArange = LoCoH.a.area(SpatialPoints(coordinates(gSp)), arange=gaSearch)
glocohA = LoCoH.a(SpatialPoints(coordinates(gSp)), a=gaSearch[16], unin = "m", unout = "km2")
glocohASf = st_as_sf(glocohA)
glocohA95Sf = glocohASf[204,]
glocohA95Sf

#h
haInit = round(max(dist(coordinates(hSp))),0)
haSearch = seq(haInit, 2*haInit, by=100)
hlocohArange = LoCoH.a.area(SpatialPoints(coordinates(hSp)), arange=haSearch)
hlocohA = LoCoH.a(SpatialPoints(coordinates(hSp)), a=haSearch[20], unin = "m", unout = "km2")
hlocohASf = st_as_sf(hlocohA)
hlocohA95Sf = hlocohASf[258,]
hlocohA95Sf

#a-LoCoH plot
alocoh = c(0.88, 1.49, 1.40, 1.64, 2.34, 2.34, 2.81, 2.66)
plot(xvals, alocoh)
```

Next I tried a different sigma value in my simulations to determine how that may influence my home range estimations in the Claiborne Lock and Dam tailrace. I then created home range estimates using the minimum convex polygon method and a plot of the values to compare to the first sigma I used.
```{r}
set.seed(6)
a2 <- simm.mou(1:25, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0003, 0.0003)),
              burst="Variable attraction")

b2 <- simm.mou(1:50, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0003, 0.0003)),
              burst="Variable attraction")

c2 <- simm.mou(1:75, b=c(-87.5526154,31.61337824),sigma = diag(c(0.0003, 0.0003)),
              burst="Variable attraction")

d2 <- simm.mou(1:100, b=c(-87.5526154,31.61337824),sigma = diag(c(0.0003, 0.0003)),
              burst="Variable attraction")

e2 <- simm.mou(1:150, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0003, 0.0003)),
              burst="Variable attraction")

f2 <- simm.mou(1:200, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0003, 0.0003)),
              burst="Variable attraction")

g2 <- simm.mou(1:250, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0003, 0.0003)),
              burst="Variable attraction")

h2 <- simm.mou(1:300, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0003, 0.0003)),
               burst = "Variable attraction")

#a
a2x = a2[[1]][["x"]]
a2y = a2[[1]][["y"]]

a2df = data.frame(a2x,a2y)
a2df = st_as_sf(x=a2df, coords=c('a2x', 'a2y'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
a2df = st_transform(a2df, crs = st_crs(6345))
a2df = a2df %>% 
  mutate(id = 1)
a2Sp = as(a2df, 'Spatial')
a2mcp95 = mcp(a2Sp, percent = 95, unin='m', unout='km2')
a2mcp95


#b
b2x = b2[[1]][["x"]]
b2y = b2[[1]][["y"]]

b2df = data.frame(b2x,b2y)
b2df = st_as_sf(x=b2df, coords=c('b2x', 'b2y'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
b2df = st_transform(b2df, crs = st_crs(6345))
b2df = b2df %>% 
  mutate(id = 1)
b2Sp = as(b2df, 'Spatial')
b2mcp95 = mcp(b2Sp, percent = 95, unin='m', unout='km2')
b2mcp95

#c
c2x = c2[[1]][["x"]]
c2y = c2[[1]][["y"]]

c2df = data.frame(c2x,c2y)
c2df = st_as_sf(x=c2df, coords=c('c2x', 'c2y'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
c2df = st_transform(c2df, crs = st_crs(6345))
c2df = c2df %>% 
  mutate(id = 1)
c2Sp = as(c2df, 'Spatial')
c2mcp95 = mcp(c2Sp, percent = 95, unin='m', unout='km2')
c2mcp95

#d
d2x = d2[[1]][["x"]]
d2y = d2[[1]][["y"]]

d2df = data.frame(d2x,d2y)
d2df = st_as_sf(x=d2df, coords=c('d2x', 'd2y'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
d2df = st_transform(d2df, crs = st_crs(6345))
d2df = d2df %>% 
  mutate(id = 1)
d2Sp = as(d2df, 'Spatial')
d2mcp95 = mcp(d2Sp, percent = 95, unin='m', unout='km2')
d2mcp95

#e
e2x = e2[[1]][["x"]]
e2y = e2[[1]][["y"]]

e2df = data.frame(e2x,e2y)
e2df = st_as_sf(x=e2df, coords=c('e2x', 'e2y'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
e2df = st_transform(e2df, crs = st_crs(6345))
e2df = e2df %>% 
  mutate(id = 1)
e2Sp = as(e2df, 'Spatial')
e2mcp95 = mcp(e2Sp, percent = 95, unin='m', unout='km2')
e2mcp95

#f
f2x = f2[[1]][["x"]]
f2y = f2[[1]][["y"]]

f2df = data.frame(f2x,f2y)
f2df = st_as_sf(x=f2df, coords=c('f2x', 'f2y'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
f2df = st_transform(f2df, crs = st_crs(6345))
f2df = f2df %>% 
  mutate(id = 1)
f2Sp = as(f2df, 'Spatial')
f2mcp95 = mcp(f2Sp, percent = 95, unin='m', unout='km2')
f2mcp95

#g
g2x = g2[[1]][["x"]]
g2y = g2[[1]][["y"]]

g2df = data.frame(g2x,g2y)
g2df = st_as_sf(x=g2df, coords=c('g2x', 'g2y'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
g2df = st_transform(g2df, crs = st_crs(6345))
g2df = g2df %>% 
  mutate(id = 1)
g2Sp = as(g2df, 'Spatial')
g2mcp95 = mcp(g2Sp, percent = 95, unin='m', unout='km2')
g2mcp95

#h
h2x = h2[[1]][["x"]]
h2y = h2[[1]][["y"]]

h2df = data.frame(h2x,h2y)
h2df = st_as_sf(x=h2df, coords=c('h2x', 'h2y'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
h2df = st_transform(h2df, crs = st_crs(6345))
h2df = h2df %>% 
  mutate(id = 1)
h2Sp = as(h2df, 'Spatial')
h2mcp95 = mcp(h2Sp, percent = 95, unin='m', unout='km2')
h2mcp95

##plot of mcp
mcps2 = c(a2mcp95$area, b2mcp95$area, c2mcp95$area, d2mcp95$area, e2mcp95$area, f2mcp95$area, g2mcp95$area, h2mcp95$area)
xvals = c(25, 50, 75, 100, 150, 200, 250, 300)
plot(xvals, mcps2)
```

I then moved into the main analysis of my paper which was calculating home range values for each simulated number of points (25-300) using 5 or 10 replicates of each of the home range estimation methods. I then plotted the mean value of the replicates for each simulated number of points (along with standard error) to analyze where the plateau occured in estimated home range size.

First code to generate the replicates. Note: The order of the simulations is not in alphabetical order because I set the seed and since I ran c, d, e, f first I needed to add in a, b, g, h at the bottom to avoid changing the values for c, d, e, f. 
```{r}
set.seed(6)
c <- replicate(10,simm.mou(1:75, b=c(-87.5526154,31.61337824),sigma = diag(c(0.0036, 0.0036)),
              burst="Variable attraction"))
d <- replicate(10,simm.mou(1:100, b=c(-87.5526154,31.61337824),sigma = diag(c(0.0036, 0.0036)),
              burst="Variable attraction"))
e <- replicate(10,simm.mou(1:150, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0036, 0.0036)),
              burst="Variable attraction"))
f <- replicate(10,simm.mou(1:200, b=c(-87.5526154,31.61337824), sigma = diag(c(0.0036, 0.0036)),
              burst="Variable attraction"))
a <- replicate(10,simm.mou(1:25, b=c(-87.5526154,31.61337824),sigma = diag(c(0.0036, 0.0036)),
                           burst="Variable attraction"))
b <- replicate(10,simm.mou(1:50, b=c(-87.5526154,31.61337824),sigma = diag(c(0.0036, 0.0036)),
                           burst="Variable attraction"))
g <- replicate(10,simm.mou(1:250, b=c(-87.5526154,31.61337824),sigma = diag(c(0.0036, 0.0036)),
                           burst="Variable attraction"))
h <- replicate(10,simm.mou(1:300, b=c(-87.5526154,31.61337824),sigma = diag(c(0.0036, 0.0036)),
                           burst="Variable attraction"))
```

Replicates and plot for estimates using the minimum convext polygon method. I ran 10 replicates and could not figure out how to get a for loop to work so I ran each one manually.
```{r}
#mcpr
#a1
ax1 = a[[1]][["x"]]
ay1 = a[[1]][["y"]]

adf1 = data.frame(ax1,ay1)
adf1 = st_as_sf(x=adf1, coords=c('ax1', 'ay1'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
adf1 = st_transform(adf1, crs = st_crs(6345))
adf1 = adf1 %>% 
  mutate(id = 1)
aSp1 = as(adf1, 'Spatial')
amcp951 = mcp(aSp1, percent = 95, unin='m', unout='km2')
amcp951

#a2
ax2 = a[[2]][["x"]]
ay2 = a[[2]][["y"]]

adf2 = data.frame(ax2,ay2)
adf2 = st_as_sf(x=adf2, coords=c('ax2', 'ay2'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
adf2 = st_transform(adf2, crs = st_crs(6345))
adf2 = adf2 %>% 
  mutate(id = 1)
aSp2 = as(adf2, 'Spatial')
amcp952 = mcp(aSp2, percent = 95, unin='m', unout='km2')
amcp952

#a3
ax3 = a[[3]][["x"]]
ay3 = a[[3]][["y"]]

adf3 = data.frame(ax3,ay3)
adf3 = st_as_sf(x=adf3, coords=c('ax3', 'ay3'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
adf3 = st_transform(adf3, crs = st_crs(6345))
adf3 = adf3 %>% 
  mutate(id = 1)
aSp3 = as(adf3, 'Spatial')
amcp953 = mcp(aSp3, percent = 95, unin='m', unout='km2')
amcp953

#a4
ax4 = a[[4]][["x"]]
ay4 = a[[4]][["y"]]

adf4 = data.frame(ax4,ay4)
adf4 = st_as_sf(x=adf4, coords=c('ax4', 'ay4'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
adf4 = st_transform(adf4, crs = st_crs(6345))
adf4 = adf4 %>% 
  mutate(id = 1)
aSp4 = as(adf4, 'Spatial')
amcp954 = mcp(aSp4, percent = 95, unin='m', unout='km2')
amcp954

#a5
ax5 = a[[5]][["x"]]
ay5 = a[[5]][["y"]]

adf5 = data.frame(ax5,ay5)
adf5 = st_as_sf(x=adf5, coords=c('ax5', 'ay5'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
adf5 = st_transform(adf5, crs = st_crs(6345))
adf5 = adf5 %>% 
  mutate(id = 1)
aSp5 = as(adf5, 'Spatial')
amcp955 = mcp(aSp5, percent = 95, unin='m', unout='km2')
amcp955

#a6
ax6 = a[[6]][["x"]]
ay6 = a[[6]][["y"]]

adf6 = data.frame(ax6,ay6)
adf6 = st_as_sf(x=adf6, coords=c('ax6', 'ay6'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
adf6 = st_transform(adf6, crs = st_crs(6345))
adf6 = adf6 %>% 
  mutate(id = 1)
aSp6 = as(adf6, 'Spatial')
amcp956 = mcp(aSp6, percent = 95, unin='m', unout='km2')
amcp956

#a7
ax7 = a[[7]][["x"]]
ay7 = a[[7]][["y"]]

adf7 = data.frame(ax7,ay7)
adf7 = st_as_sf(x=adf7, coords=c('ax7', 'ay7'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
adf7 = st_transform(adf7, crs = st_crs(6345))
adf7 = adf7 %>% 
  mutate(id = 1)
aSp7 = as(adf7, 'Spatial')
amcp957 = mcp(aSp7, percent = 95, unin='m', unout='km2')
amcp957

#a8
ax8 = a[[8]][["x"]]
ay8 = a[[8]][["y"]]

adf8 = data.frame(ax8,ay8)
adf8 = st_as_sf(x=adf8, coords=c('ax8', 'ay8'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
adf8 = st_transform(adf8, crs = st_crs(6345))
adf8 = adf8 %>% 
  mutate(id = 1)
aSp8 = as(adf8, 'Spatial')
amcp958 = mcp(aSp8, percent = 95, unin='m', unout='km2')
amcp958

#a9
ax9 = a[[9]][["x"]]
ay9 = a[[9]][["y"]]

adf9 = data.frame(ax9,ay9)
adf9 = st_as_sf(x=adf9, coords=c('ax9', 'ay9'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
adf9 = st_transform(adf9, crs = st_crs(6345))
adf9 = adf9 %>% 
  mutate(id = 1)
aSp9 = as(adf9, 'Spatial')
amcp959 = mcp(aSp9, percent = 95, unin='m', unout='km2')
amcp959

#a10
ax10 = a[[10]][["x"]]
ay10 = a[[10]][["y"]]

adf10 = data.frame(ax10,ay10)
adf10 = st_as_sf(x=adf10, coords=c('ax10', 'ay10'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
adf10 = st_transform(adf10, crs = st_crs(6345))
adf10 = adf10 %>% 
  mutate(id = 1)
aSp10 = as(adf10, 'Spatial')
amcp9510 = mcp(aSp10, percent = 95, unin='m', unout='km2')
amcp9510

amcpr = c(amcp951, amcp952, amcp953, amcp953, amcp955, amcp956, amcp957, amcp958, amcp959, amcp9510)
amcpr = c(1.197209, 0.6964358, 1.07218, 1.07218, 1.791486, 0.941122, 2.130329, 0.5753616, 0.7308309, 1.356868)

#b1
bx1 = b[[1]][["x"]]
by1 = b[[1]][["y"]]

bdf1 = data.frame(bx1,by1)
bdf1 = st_as_sf(x=bdf1, coords=c('bx1', 'by1'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
bdf1 = st_transform(bdf1, crs = st_crs(6345))
bdf1 = bdf1 %>% 
  mutate(id = 1)
bSp1 = as(bdf1, 'Spatial')
bmcp951 = mcp(bSp1, percent = 95, unin='m', unout='km2')
bmcp951

#b2
bx2 = b[[2]][["x"]]
by2 = b[[2]][["y"]]

bdf2 = data.frame(bx2,by2)
bdf2 = st_as_sf(x=bdf2, coords=c('bx2', 'by2'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
bdf2 = st_transform(bdf2, crs = st_crs(6345))
bdf2 = bdf2 %>% 
  mutate(id = 1)
bSp2 = as(bdf2, 'Spatial')
bmcp952 = mcp(bSp2, percent = 95, unin='m', unout='km2')
bmcp952

#b3
bx3 = b[[3]][["x"]]
by3 = b[[3]][["y"]]

bdf3 = data.frame(bx3,by3)
bdf3 = st_as_sf(x=bdf3, coords=c('bx3', 'by3'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
bdf3 = st_transform(bdf3, crs = st_crs(6345))
bdf3 = bdf3 %>% 
  mutate(id = 1)
bSp3 = as(bdf3, 'Spatial')
bmcp953 = mcp(bSp3, percent = 95, unin='m', unout='km2')
bmcp953

#b4
bx4 = b[[4]][["x"]]
by4 = b[[4]][["y"]]

bdf4 = data.frame(bx4,by4)
bdf4 = st_as_sf(x=bdf4, coords=c('bx4', 'by4'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
bdf4 = st_transform(bdf4, crs = st_crs(6345))
bdf4 = bdf4 %>% 
  mutate(id = 1)
bSp4 = as(bdf4, 'Spatial')
bmcp954 = mcp(bSp4, percent = 95, unin='m', unout='km2')
bmcp954

#b5
bx5 = b[[5]][["x"]]
by5 = b[[5]][["y"]]

bdf5 = data.frame(bx5,by5)
bdf5 = st_as_sf(x=bdf5, coords=c('bx5', 'by5'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
bdf5 = st_transform(bdf5, crs = st_crs(6345))
bdf5 = bdf5 %>% 
  mutate(id = 1)
bSp5 = as(bdf5, 'Spatial')
bmcp955 = mcp(bSp5, percent = 95, unin='m', unout='km2')
bmcp955

#b6
bx6 = b[[6]][["x"]]
by6 = b[[6]][["y"]]

bdf6 = data.frame(bx6,by6)
bdf6 = st_as_sf(x=bdf6, coords=c('bx6', 'by6'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
bdf6 = st_transform(bdf6, crs = st_crs(6345))
bdf6 = bdf6 %>% 
  mutate(id = 1)
bSp6 = as(bdf6, 'Spatial')
bmcp956 = mcp(bSp6, percent = 95, unin='m', unout='km2')
bmcp956

#b7
bx7 = b[[7]][["x"]]
by7 = b[[7]][["y"]]

bdf7 = data.frame(bx7,by7)
bdf7 = st_as_sf(x=bdf7, coords=c('bx7', 'by7'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
bdf7 = st_transform(bdf7, crs = st_crs(6345))
bdf7 = bdf7 %>% 
  mutate(id = 1)
bSp7 = as(bdf7, 'Spatial')
bmcp957 = mcp(bSp7, percent = 95, unin='m', unout='km2')
bmcp957

#b8
bx8 = b[[8]][["x"]]
by8 = b[[8]][["y"]]

bdf8 = data.frame(bx8,by8)
bdf8 = st_as_sf(x=bdf8, coords=c('bx8', 'by8'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
bdf8 = st_transform(bdf8, crs = st_crs(6345))
bdf8 = bdf8 %>% 
  mutate(id = 1)
bSp8 = as(bdf8, 'Spatial')
bmcp958 = mcp(bSp8, percent = 95, unin='m', unout='km2')
bmcp958

#b9
bx9 = b[[9]][["x"]]
by9 = b[[9]][["y"]]

bdf9 = data.frame(bx9,by9)
bdf9 = st_as_sf(x=bdf9, coords=c('bx9', 'by9'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
bdf9 = st_transform(bdf9, crs = st_crs(6345))
bdf9 = bdf9 %>% 
  mutate(id = 1)
bSp9 = as(bdf9, 'Spatial')
bmcp959 = mcp(bSp9, percent = 95, unin='m', unout='km2')
bmcp959

#b10
bx10 = b[[10]][["x"]]
by10 = b[[10]][["y"]]

bdf10 = data.frame(bx10,by10)
bdf10 = st_as_sf(x=bdf10, coords=c('bx10', 'by10'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
bdf10 = st_transform(bdf10, crs = st_crs(6345))
bdf10 = bdf10 %>% 
  mutate(id = 1)
bSp10 = as(bdf10, 'Spatial')
bmcp9510 = mcp(bSp10, percent = 95, unin='m', unout='km2')
bmcp9510

bmcpr = c(bmcp951, bmcp952, bmcp953, bmcp953, bmcp955, bmcp956, bmcp957, bmcp958, bmcp959, bmcp9510)
bmcpr = c(1.468075, 2.276676, 1.473686, 1.473686, 2.218867, 1.938019, 1.942093, 1.701421, 1.37549, 1.492744)

#c1
cx1 = c[[1]][["x"]]
cy1 = c[[1]][["y"]]

cdf1 = data.frame(cx1,cy1)
cdf1 = st_as_sf(x=cdf1, coords=c('cx1', 'cy1'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
cdf1 = st_transform(cdf1, crs = st_crs(6345))
cdf1 = cdf1 %>% 
  mutate(id = 1)
cSp1 = as(cdf1, 'Spatial')
cmcp951 = mcp(cSp1, percent = 95, unin='m', unout='km2')
cmcp951

#c2
cx2 = c[[2]][["x"]]
cy2 = c[[2]][["y"]]

cdf2 = data.frame(cx2,cy2)
cdf2 = st_as_sf(x=cdf2, coords=c('cx2', 'cy2'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
cdf2 = st_transform(cdf2, crs = st_crs(6345))
cdf2 = cdf2 %>% 
  mutate(id = 1)
cSp2 = as(cdf2, 'Spatial')
cmcp952 = mcp(cSp2, percent = 95, unin='m', unout='km2')
cmcp952

#c3
cx3 = c[[3]][["x"]]
cy3 = c[[3]][["y"]]

cdf3 = data.frame(cx3,cy3)
cdf3 = st_as_sf(x=cdf3, coords=c('cx3', 'cy3'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
cdf3 = st_transform(cdf3, crs = st_crs(6345))
cdf3 = cdf3 %>% 
  mutate(id = 1)
cSp3 = as(cdf3, 'Spatial')
cmcp953 = mcp(cSp3, percent = 95, unin='m', unout='km2')
cmcp953

#c4
cx4 = c[[4]][["x"]]
cy4 = c[[4]][["y"]]

cdf4 = data.frame(cx4,cy4)
cdf4 = st_as_sf(x=cdf4, coords=c('cx4', 'cy4'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
cdf4 = st_transform(cdf4, crs = st_crs(6345))
cdf4 = cdf4 %>% 
  mutate(id = 1)
cSp4 = as(cdf4, 'Spatial')
cmcp954 = mcp(cSp4, percent = 95, unin='m', unout='km2')
cmcp954

#c5
cx5 = c[[5]][["x"]]
cy5 = c[[5]][["y"]]

cdf5 = data.frame(cx5,cy5)
cdf5 = st_as_sf(x=cdf5, coords=c('cx5', 'cy5'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
cdf5 = st_transform(cdf5, crs = st_crs(6345))
cdf5 = cdf5 %>% 
  mutate(id = 1)
cSp5 = as(cdf5, 'Spatial')
cmcp955 = mcp(cSp5, percent = 95, unin='m', unout='km2')
cmcp955

#c6
cx6 = c[[6]][["x"]]
cy6 = c[[6]][["y"]]

cdf6 = data.frame(cx6,cy6)
cdf6 = st_as_sf(x=cdf6, coords=c('cx6', 'cy6'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
cdf6 = st_transform(cdf6, crs = st_crs(6345))
cdf6 = cdf6 %>% 
  mutate(id = 1)
cSp6 = as(cdf6, 'Spatial')
cmcp956 = mcp(cSp6, percent = 95, unin='m', unout='km2')
cmcp956

#c7
cx7 = c[[7]][["x"]]
cy7 = c[[7]][["y"]]

cdf7 = data.frame(cx7,cy7)
cdf7 = st_as_sf(x=cdf7, coords=c('cx7', 'cy7'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
cdf7 = st_transform(cdf7, crs = st_crs(6345))
cdf7 = cdf7 %>% 
  mutate(id = 1)
cSp7 = as(cdf7, 'Spatial')
cmcp957 = mcp(cSp7, percent = 95, unin='m', unout='km2')
cmcp957

#c8
cx8 = c[[8]][["x"]]
cy8 = c[[8]][["y"]]

cdf8 = data.frame(cx8,cy8)
cdf8 = st_as_sf(x=cdf8, coords=c('cx8', 'cy8'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
cdf8 = st_transform(cdf8, crs = st_crs(6345))
cdf8 = cdf8 %>% 
  mutate(id = 1)
cSp8 = as(cdf8, 'Spatial')
cmcp958 = mcp(cSp8, percent = 95, unin='m', unout='km2')
cmcp958

#c9
cx9 = c[[9]][["x"]]
cy9 = c[[9]][["y"]]

cdf9 = data.frame(cx9,cy9)
cdf9 = st_as_sf(x=cdf9, coords=c('cx9', 'cy9'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
cdf9 = st_transform(cdf9, crs = st_crs(6345))
cdf9 = cdf9 %>% 
  mutate(id = 1)
cSp9 = as(cdf9, 'Spatial')
cmcp959 = mcp(cSp9, percent = 95, unin='m', unout='km2')
cmcp959

#c10
cx10 = c[[10]][["x"]]
cy10 = c[[10]][["y"]]

cdf10 = data.frame(cx10,cy10)
cdf10 = st_as_sf(x=cdf10, coords=c('cx10', 'cy10'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
cdf10 = st_transform(cdf10, crs = st_crs(6345))
cdf10 = cdf10 %>% 
  mutate(id = 1)
cSp10 = as(cdf10, 'Spatial')
cmcp9510 = mcp(cSp10, percent = 95, unin='m', unout='km2')
cmcp9510

cmcpr = c(cmcp951, cmcp952, cmcp953, cmcp953, cmcp955, cmcp956, cmcp957, cmcp958, cmcp959, cmcp9510)
cmcpr = c(1.977485, 1.543886, 1.73541, 1.73541, 2.394656, 1.949021, 2.627219, 1.659036, 2.223331, 2.506538)

#d1
dx1 = d[[1]][["x"]]
dy1 = d[[1]][["y"]]

ddf1 = data.frame(dx1,dy1)
ddf1 = st_as_sf(x=ddf1, coords=c('dx1', 'dy1'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
ddf1 = st_transform(ddf1, crs = st_crs(6345))
ddf1 = ddf1 %>% 
  mutate(id = 1)
dSp1 = as(ddf1, 'Spatial')
dmcp951 = mcp(dSp1, percent = 95, unin='m', unout='km2')
dmcp951

#d2
dx2 = d[[2]][["x"]]
dy2 = d[[2]][["y"]]

ddf2 = data.frame(dx2,dy2)
ddf2 = st_as_sf(x=ddf2, coords=c('dx2', 'dy2'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
ddf2 = st_transform(ddf2, crs = st_crs(6345))
ddf2 = ddf2 %>% 
  mutate(id = 1)
dSp2 = as(ddf2, 'Spatial')
dmcp952 = mcp(dSp2, percent = 95, unin='m', unout='km2')
dmcp952

#d3
dx3 = d[[3]][["x"]]
dy3 = d[[3]][["y"]]

ddf3 = data.frame(dx3,dy3)
ddf3 = st_as_sf(x=ddf3, coords=c('dx3', 'dy3'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
ddf3 = st_transform(ddf3, crs = st_crs(6345))
ddf3 = ddf3 %>% 
  mutate(id = 1)
dSp3 = as(ddf3, 'Spatial')
dmcp953 = mcp(dSp3, percent = 95, unin='m', unout='km2')
dmcp953

#d4
dx4 = d[[4]][["x"]]
dy4 = d[[4]][["y"]]

ddf4 = data.frame(dx4,dy4)
ddf4 = st_as_sf(x=ddf4, coords=c('dx4', 'dy4'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
ddf4 = st_transform(ddf4, crs = st_crs(6345))
ddf4 = ddf4 %>% 
  mutate(id = 1)
dSp4 = as(ddf4, 'Spatial')
dmcp954 = mcp(dSp4, percent = 95, unin='m', unout='km2')
dmcp954

#d5
dx5 = d[[5]][["x"]]
dy5 = d[[5]][["y"]]

ddf5 = data.frame(dx5,dy5)
ddf5 = st_as_sf(x=ddf5, coords=c('dx5', 'dy5'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
ddf5 = st_transform(ddf5, crs = st_crs(6345))
ddf5 = ddf5 %>% 
  mutate(id = 1)
dSp5 = as(ddf5, 'Spatial')
dmcp955 = mcp(dSp5, percent = 95, unin='m', unout='km2')
dmcp955

#d6
dx6 = d[[6]][["x"]]
dy6 = d[[6]][["y"]]

ddf6 = data.frame(dx6,dy6)
ddf6 = st_as_sf(x=ddf6, coords=c('dx6', 'dy6'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
ddf6 = st_transform(ddf6, crs = st_crs(6345))
ddf6 = ddf6 %>% 
  mutate(id = 1)
dSp6 = as(ddf6, 'Spatial')
dmcp956 = mcp(dSp6, percent = 95, unin='m', unout='km2')
dmcp956

#d7
dx7 = d[[7]][["x"]]
dy7 = d[[7]][["y"]]

ddf7 = data.frame(dx7,dy7)
ddf7 = st_as_sf(x=ddf7, coords=c('dx7', 'dy7'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
ddf7 = st_transform(ddf7, crs = st_crs(6345))
ddf7 = ddf7 %>% 
  mutate(id = 1)
dSp7 = as(ddf7, 'Spatial')
dmcp957 = mcp(dSp7, percent = 95, unin='m', unout='km2')
dmcp957

#d8
dx8 = d[[8]][["x"]]
dy8 = d[[8]][["y"]]

ddf8 = data.frame(dx8,dy8)
ddf8 = st_as_sf(x=ddf8, coords=c('dx8', 'dy8'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
ddf8 = st_transform(ddf8, crs = st_crs(6345))
ddf8 = ddf8 %>% 
  mutate(id = 1)
dSp8 = as(ddf8, 'Spatial')
dmcp958 = mcp(dSp8, percent = 95, unin='m', unout='km2')
dmcp958

#d9
dx9 = d[[9]][["x"]]
dy9 = d[[9]][["y"]]

ddf9 = data.frame(dx9,dy9)
ddf9 = st_as_sf(x=ddf9, coords=c('dx9', 'dy9'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
ddf9 = st_transform(ddf9, crs = st_crs(6345))
ddf9 = ddf9 %>% 
  mutate(id = 1)
dSp9 = as(ddf9, 'Spatial')
dmcp959 = mcp(dSp9, percent = 95, unin='m', unout='km2')
dmcp959

#d10
dx10 = d[[10]][["x"]]
dy10 = d[[10]][["y"]]

ddf10 = data.frame(dx10,dy10)
ddf10 = st_as_sf(x=ddf10, coords=c('dx10', 'dy10'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
ddf10 = st_transform(ddf10, crs = st_crs(6345))
ddf10 = ddf10 %>% 
  mutate(id = 1)
dSp10 = as(ddf10, 'Spatial')
dmcp9510 = mcp(dSp10, percent = 95, unin='m', unout='km2')
dmcp9510

dmcpr = c(dmcp951, dmcp952, dmcp953, dmcp953, dmcp955, dmcp956, dmcp957, dmcp958, dmcp959, dmcp9510)
dmcpr = c(2.236249, 2.081231, 2.324957, 2.324957, 3.160921, 1.80207, 2.704384, 2.091046, 1.87733, 2.400218)

#e1
ex1 = e[[1]][["x"]]
ey1 = e[[1]][["y"]]

edf1 = data.frame(ex1,ey1)
edf1 = st_as_sf(x=edf1, coords=c('ex1', 'ey1'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
edf1 = st_transform(edf1, crs = st_crs(6345))
edf1 = edf1 %>% 
  mutate(id = 1)
eSp1 = as(edf1, 'Spatial')
emcp951 = mcp(eSp1, percent = 95, unin='m', unout='km2')
emcp951

#e2
ex2 = e[[2]][["x"]]
ey2 = e[[2]][["y"]]

edf2 = data.frame(ex2,ey2)
edf2 = st_as_sf(x=edf2, coords=c('ex2', 'ey2'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
edf2 = st_transform(edf2, crs = st_crs(6345))
edf2 = edf2 %>% 
  mutate(id = 1)
eSp2 = as(edf2, 'Spatial')
emcp952 = mcp(eSp2, percent = 95, unin='m', unout='km2')
emcp952

#e3
ex3 = e[[3]][["x"]]
ey3 = e[[3]][["y"]]

edf3 = data.frame(ex3,ey3)
edf3 = st_as_sf(x=edf3, coords=c('ex3', 'ey3'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
edf3 = st_transform(edf3, crs = st_crs(6345))
edf3 = edf3 %>% 
  mutate(id = 1)
eSp3 = as(edf3, 'Spatial')
emcp953 = mcp(eSp3, percent = 95, unin='m', unout='km2')
emcp953

#e4
ex4 = e[[4]][["x"]]
ey4 = e[[4]][["y"]]

edf4 = data.frame(ex4,ey4)
edf4 = st_as_sf(x=edf4, coords=c('ex4', 'ey4'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
edf4 = st_transform(edf4, crs = st_crs(6345))
edf4 = edf4 %>% 
  mutate(id = 1)
eSp4 = as(edf4, 'Spatial')
emcp954 = mcp(eSp4, percent = 95, unin='m', unout='km2')
emcp954

#e5
ex5 = e[[5]][["x"]]
ey5 = e[[5]][["y"]]

edf5 = data.frame(ex5,ey5)
edf5 = st_as_sf(x=edf5, coords=c('ex5', 'ey5'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
edf5 = st_transform(edf5, crs = st_crs(6345))
edf5 = edf5 %>% 
  mutate(id = 1)
eSp5 = as(edf5, 'Spatial')
emcp955 = mcp(eSp5, percent = 95, unin='m', unout='km2')
emcp955

#e6
ex6 = e[[6]][["x"]]
ey6 = e[[6]][["y"]]

edf6 = data.frame(ex6,ey6)
edf6 = st_as_sf(x=edf6, coords=c('ex6', 'ey6'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
edf6 = st_transform(edf6, crs = st_crs(6345))
edf6 = edf6 %>% 
  mutate(id = 1)
eSp6 = as(edf6, 'Spatial')
emcp956 = mcp(eSp6, percent = 95, unin='m', unout='km2')
emcp956

#e7
ex7 = e[[7]][["x"]]
ey7 = e[[7]][["y"]]

edf7 = data.frame(ex7,ey7)
edf7 = st_as_sf(x=edf7, coords=c('ex7', 'ey7'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
edf7 = st_transform(edf7, crs = st_crs(6345))
edf7 = edf7 %>% 
  mutate(id = 1)
eSp7 = as(edf7, 'Spatial')
emcp957 = mcp(eSp7, percent = 95, unin='m', unout='km2')
emcp957

#e8
ex8 = e[[8]][["x"]]
ey8 = e[[8]][["y"]]

edf8 = data.frame(ex8,ey8)
edf8 = st_as_sf(x=edf8, coords=c('ex8', 'ey8'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
edf8 = st_transform(edf8, crs = st_crs(6345))
edf8 = edf8 %>% 
  mutate(id = 1)
eSp8 = as(edf8, 'Spatial')
emcp958 = mcp(eSp8, percent = 95, unin='m', unout='km2')
emcp958

#e9
ex9 = e[[9]][["x"]]
ey9 = e[[9]][["y"]]

edf9 = data.frame(ex9,ey9)
edf9 = st_as_sf(x=edf9, coords=c('ex9', 'ey9'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
edf9 = st_transform(edf9, crs = st_crs(6345))
edf9 = edf9 %>% 
  mutate(id = 1)
eSp9 = as(edf9, 'Spatial')
emcp959 = mcp(eSp9, percent = 95, unin='m', unout='km2')
emcp959

#e10
ex10 = e[[10]][["x"]]
ey10 = e[[10]][["y"]]

edf10 = data.frame(ex10,ey10)
edf10 = st_as_sf(x=edf10, coords=c('ex10', 'ey10'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
edf10 = st_transform(edf10, crs = st_crs(6345))
edf10 = edf10 %>% 
  mutate(id = 1)
eSp10 = as(edf10, 'Spatial')
emcp9510 = mcp(eSp10, percent = 95, unin='m', unout='km2')
emcp9510

emcpr = c(emcp951, emcp952, emcp953, emcp954, emcp955, emcp956, emcp957, emcp958, emcp959, emcp9510)
emcpr = c(1.908731, 2.760063, 2.292604, 2.002508, 2.301427, 2.181799, 2.397608, 2.065257, 2.9055, 1.973988)

#f1
fx1 = f[[1]][["x"]]
fy1 = f[[1]][["y"]]

fdf1 = data.frame(fx1,fy1)
fdf1 = st_as_sf(x=fdf1, coords=c('fx1', 'fy1'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
fdf1 = st_transform(fdf1, crs = st_crs(6345))
fdf1 = fdf1 %>% 
  mutate(id = 1)
fSp1 = as(fdf1, 'Spatial')
fmcp951 = mcp(fSp1, percent = 95, unin='m', unout='km2')
fmcp951

#f2
fx2 = f[[2]][["x"]]
fy2 = f[[2]][["y"]]

fdf2 = data.frame(fx2,fy2)
fdf2 = st_as_sf(x=fdf2, coords=c('fx2', 'fy2'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
fdf2 = st_transform(fdf2, crs = st_crs(6345))
fdf2 = fdf2 %>% 
  mutate(id = 1)
fSp2 = as(fdf2, 'Spatial')
fmcp952 = mcp(fSp2, percent = 95, unin='m', unout='km2')
fmcp952

#f3
fx3 = f[[3]][["x"]]
fy3 = f[[3]][["y"]]

fdf3 = data.frame(fx3,fy3)
fdf3 = st_as_sf(x=fdf3, coords=c('fx3', 'fy3'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
fdf3 = st_transform(fdf3, crs = st_crs(6345))
fdf3 = fdf3 %>% 
  mutate(id = 1)
fSp3 = as(fdf3, 'Spatial')
fmcp953 = mcp(fSp3, percent = 95, unin='m', unout='km2')
fmcp953

#f4
fx4 = f[[4]][["x"]]
fy4 = f[[4]][["y"]]

fdf4 = data.frame(fx4,fy4)
fdf4 = st_as_sf(x=fdf4, coords=c('fx4', 'fy4'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
fdf4 = st_transform(fdf4, crs = st_crs(6345))
fdf4 = fdf4 %>% 
  mutate(id = 1)
fSp4 = as(fdf4, 'Spatial')
fmcp954 = mcp(fSp4, percent = 95, unin='m', unout='km2')
fmcp954

#f5
fx5 = f[[5]][["x"]]
fy5 = f[[5]][["y"]]

fdf5 = data.frame(fx5,fy5)
fdf5 = st_as_sf(x=fdf5, coords=c('fx5', 'fy5'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
fdf5 = st_transform(fdf5, crs = st_crs(6345))
fdf5 = fdf5 %>% 
  mutate(id = 1)
fSp5 = as(fdf5, 'Spatial')
fmcp955 = mcp(fSp5, percent = 95, unin='m', unout='km2')
fmcp955

#f6
fx6 = f[[6]][["x"]]
fy6 = f[[6]][["y"]]

fdf6 = data.frame(fx6,fy6)
fdf6 = st_as_sf(x=fdf6, coords=c('fx6', 'fy6'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
fdf6 = st_transform(fdf6, crs = st_crs(6345))
fdf6 = fdf6 %>% 
  mutate(id = 1)
fSp6 = as(fdf6, 'Spatial')
fmcp956 = mcp(fSp6, percent = 95, unin='m', unout='km2')
fmcp956

#f7
fx7 = f[[7]][["x"]]
fy7 = f[[7]][["y"]]

fdf7 = data.frame(fx7,fy7)
fdf7 = st_as_sf(x=fdf7, coords=c('fx7', 'fy7'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
fdf7 = st_transform(fdf7, crs = st_crs(6345))
fdf7 = fdf7 %>% 
  mutate(id = 1)
fSp7 = as(fdf7, 'Spatial')
fmcp957 = mcp(fSp7, percent = 95, unin='m', unout='km2')
fmcp957

#f8
fx8 = f[[8]][["x"]]
fy8 = f[[8]][["y"]]

fdf8 = data.frame(fx8,fy8)
fdf8 = st_as_sf(x=fdf8, coords=c('fx8', 'fy8'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
fdf8 = st_transform(fdf8, crs = st_crs(6345))
fdf8 = fdf8 %>% 
  mutate(id = 1)
fSp8 = as(fdf8, 'Spatial')
fmcp958 = mcp(fSp8, percent = 95, unin='m', unout='km2')
fmcp958

#f9
fx9 = f[[9]][["x"]]
fy9 = f[[9]][["y"]]

fdf9 = data.frame(fx9,fy9)
fdf9 = st_as_sf(x=fdf9, coords=c('fx9', 'fy9'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
fdf9 = st_transform(fdf9, crs = st_crs(6345))
fdf9 = fdf9 %>% 
  mutate(id = 1)
fSp9 = as(fdf9, 'Spatial')
fmcp959 = mcp(fSp9, percent = 95, unin='m', unout='km2')
fmcp959

#f10
fx10 = f[[10]][["x"]]
fy10 = f[[10]][["y"]]

fdf10 = data.frame(fx10,fy10)
fdf10 = st_as_sf(x=fdf10, coords=c('fx10', 'fy10'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
fdf10 = st_transform(fdf10, crs = st_crs(6345))
fdf10 = fdf10 %>% 
  mutate(id = 1)
fSp10 = as(fdf10, 'Spatial')
fmcp9510 = mcp(fSp10, percent = 95, unin='m', unout='km2')
fmcp9510

fmcpr = c(fmcp951, fmcp952, fmcp953, fmcp953, fmcp955, fmcp956, fmcp957, fmcp958, fmcp959, fmcp9510)
fmcpr = c(2.428763, 3.246098, 3.044447, 3.044447, 3.092492, 2.321403, 2.891613, 2.460962, 2.775681, 2.18651)

#g1
gx1 = g[[1]][["x"]]
gy1 = g[[1]][["y"]]

gdf1 = data.frame(gx1,gy1)
gdf1 = st_as_sf(x=gdf1, coords=c('gx1', 'gy1'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
gdf1 = st_transform(gdf1, crs = st_crs(6345))
gdf1 = gdf1 %>% 
  mutate(id = 1)
gSp1 = as(gdf1, 'Spatial')
gmcp951 = mcp(gSp1, percent = 95, unin='m', unout='km2')
gmcp951

#g2
gx2 = g[[2]][["x"]]
gy2 = g[[2]][["y"]]

gdf2 = data.frame(gx2,gy2)
gdf2 = st_as_sf(x=gdf2, coords=c('gx2', 'gy2'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
gdf2 = st_transform(gdf2, crs = st_crs(6345))
gdf2 = gdf2 %>% 
  mutate(id = 1)
gSp2 = as(gdf2, 'Spatial')
gmcp952 = mcp(gSp2, percent = 95, unin='m', unout='km2')
gmcp952

#g3
gx3 = g[[3]][["x"]]
gy3 = g[[3]][["y"]]

gdf3 = data.frame(gx3,gy3)
gdf3 = st_as_sf(x=gdf3, coords=c('gx3', 'gy3'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
gdf3 = st_transform(gdf3, crs = st_crs(6345))
gdf3 = gdf3 %>% 
  mutate(id = 1)
gSp3 = as(gdf3, 'Spatial')
gmcp953 = mcp(gSp3, percent = 95, unin='m', unout='km2')
gmcp953

#g4
gx4 = g[[4]][["x"]]
gy4 = g[[4]][["y"]]

gdf4 = data.frame(gx4,gy4)
gdf4 = st_as_sf(x=gdf4, coords=c('gx4', 'gy4'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
gdf4 = st_transform(gdf4, crs = st_crs(6345))
gdf4 = gdf4 %>% 
  mutate(id = 1)
gSp4 = as(gdf4, 'Spatial')
gmcp954 = mcp(gSp4, percent = 95, unin='m', unout='km2')
gmcp954

#g5
gx5 = g[[5]][["x"]]
gy5 = g[[5]][["y"]]

gdf5 = data.frame(gx5,gy5)
gdf5 = st_as_sf(x=gdf5, coords=c('gx5', 'gy5'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
gdf5 = st_transform(gdf5, crs = st_crs(6345))
gdf5 = gdf5 %>% 
  mutate(id = 1)
gSp5 = as(gdf5, 'Spatial')
gmcp955 = mcp(gSp5, percent = 95, unin='m', unout='km2')
gmcp955

#g6
gx6 = g[[6]][["x"]]
gy6 = g[[6]][["y"]]

gdf6 = data.frame(gx6,gy6)
gdf6 = st_as_sf(x=gdf6, coords=c('gx6', 'gy6'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
gdf6 = st_transform(gdf6, crs = st_crs(6345))
gdf6 = gdf6 %>% 
  mutate(id = 1)
gSp6 = as(gdf6, 'Spatial')
gmcp956 = mcp(gSp6, percent = 95, unin='m', unout='km2')
gmcp956

#g7
gx7 = g[[7]][["x"]]
gy7 = g[[7]][["y"]]

gdf7 = data.frame(gx7,gy7)
gdf7 = st_as_sf(x=gdf7, coords=c('gx7', 'gy7'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
gdf7 = st_transform(gdf7, crs = st_crs(6345))
gdf7 = gdf7 %>% 
  mutate(id = 1)
gSp7 = as(gdf7, 'Spatial')
gmcp957 = mcp(gSp7, percent = 95, unin='m', unout='km2')
gmcp957

#g8
gx8 = g[[8]][["x"]]
gy8 = g[[8]][["y"]]

gdf8 = data.frame(gx8,gy8)
gdf8 = st_as_sf(x=gdf8, coords=c('gx8', 'gy8'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
gdf8 = st_transform(gdf8, crs = st_crs(6345))
gdf8 = gdf8 %>% 
  mutate(id = 1)
gSp8 = as(gdf8, 'Spatial')
gmcp958 = mcp(gSp8, percent = 95, unin='m', unout='km2')
gmcp958

#g9
gx9 = g[[9]][["x"]]
gy9 = g[[9]][["y"]]

gdf9 = data.frame(gx9,gy9)
gdf9 = st_as_sf(x=gdf9, coords=c('gx9', 'gy9'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
gdf9 = st_transform(gdf9, crs = st_crs(6345))
gdf9 = gdf9 %>% 
  mutate(id = 1)
gSp9 = as(gdf9, 'Spatial')
gmcp959 = mcp(gSp9, percent = 95, unin='m', unout='km2')
gmcp959

#g10
gx10 = g[[10]][["x"]]
gy10 = g[[10]][["y"]]

gdf10 = data.frame(gx10,gy10)
gdf10 = st_as_sf(x=gdf10, coords=c('gx10', 'gy10'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
gdf10 = st_transform(gdf10, crs = st_crs(6345))
gdf10 = gdf10 %>% 
  mutate(id = 1)
gSp10 = as(gdf10, 'Spatial')
gmcp9510 = mcp(gSp10, percent = 95, unin='m', unout='km2')
gmcp9510

gmcpr = c(gmcp951, gmcp952, gmcp953, gmcp953, gmcp955, gmcp956, gmcp957, gmcp958, gmcp959, gmcp9510)
gmcpr = c(2.415072, 2.682696, 2.516929, 2.516929, 2.487853, 2.564221, 2.952137, 2.353423, 3.077237, 2.461938)

#h1
hx1 = h[[1]][["x"]]
hy1 = h[[1]][["y"]]

hdf1 = data.frame(hx1,hy1)
hdf1 = st_as_sf(x=hdf1, coords=c('hx1', 'hy1'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
hdf1 = st_transform(hdf1, crs = st_crs(6345))
hdf1 = hdf1 %>% 
  mutate(id = 1)
hSp1 = as(hdf1, 'Spatial')
hmcp951 = mcp(hSp1, percent = 95, unin='m', unout='km2')
hmcp951

#h2
hx2 = h[[2]][["x"]]
hy2 = h[[2]][["y"]]

hdf2 = data.frame(hx2,hy2)
hdf2 = st_as_sf(x=hdf2, coords=c('hx2', 'hy2'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
hdf2 = st_transform(hdf2, crs = st_crs(6345))
hdf2 = hdf2 %>% 
  mutate(id = 1)
hSp2 = as(hdf2, 'Spatial')
hmcp952 = mcp(hSp2, percent = 95, unin='m', unout='km2')
hmcp952

#h3
hx3 = h[[3]][["x"]]
hy3 = h[[3]][["y"]]

hdf3 = data.frame(hx3,hy3)
hdf3 = st_as_sf(x=hdf3, coords=c('hx3', 'hy3'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
hdf3 = st_transform(hdf3, crs = st_crs(6345))
hdf3 = hdf3 %>% 
  mutate(id = 1)
hSp3 = as(hdf3, 'Spatial')
hmcp953 = mcp(hSp3, percent = 95, unin='m', unout='km2')
hmcp953

#h4
hx4 = h[[4]][["x"]]
hy4 = h[[4]][["y"]]

hdf4 = data.frame(hx4,hy4)
hdf4 = st_as_sf(x=hdf4, coords=c('hx4', 'hy4'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
hdf4 = st_transform(hdf4, crs = st_crs(6345))
hdf4 = hdf4 %>% 
  mutate(id = 1)
hSp4 = as(hdf4, 'Spatial')
hmcp954 = mcp(hSp4, percent = 95, unin='m', unout='km2')
hmcp954

#h5
hx5 = h[[5]][["x"]]
hy5 = h[[5]][["y"]]

hdf5 = data.frame(hx5,hy5)
hdf5 = st_as_sf(x=hdf5, coords=c('hx5', 'hy5'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
hdf5 = st_transform(hdf5, crs = st_crs(6345))
hdf5 = hdf5 %>% 
  mutate(id = 1)
hSp5 = as(hdf5, 'Spatial')
hmcp955 = mcp(hSp5, percent = 95, unin='m', unout='km2')
hmcp955

#h6
hx6 = h[[6]][["x"]]
hy6 = h[[6]][["y"]]

hdf6 = data.frame(hx6,hy6)
hdf6 = st_as_sf(x=hdf6, coords=c('hx6', 'hy6'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
hdf6 = st_transform(hdf6, crs = st_crs(6345))
hdf6 = hdf6 %>% 
  mutate(id = 1)
hSp6 = as(hdf6, 'Spatial')
hmcp956 = mcp(hSp6, percent = 95, unin='m', unout='km2')
hmcp956

#h7
hx7 = h[[7]][["x"]]
hy7 = h[[7]][["y"]]

hdf7 = data.frame(hx7,hy7)
hdf7 = st_as_sf(x=hdf7, coords=c('hx7', 'hy7'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
hdf7 = st_transform(hdf7, crs = st_crs(6345))
hdf7 = hdf7 %>% 
  mutate(id = 1)
hSp7 = as(hdf7, 'Spatial')
hmcp957 = mcp(hSp7, percent = 95, unin='m', unout='km2')
hmcp957

#h8
hx8 = h[[8]][["x"]]
hy8 = h[[8]][["y"]]

hdf8 = data.frame(hx8,hy8)
hdf8 = st_as_sf(x=hdf8, coords=c('hx8', 'hy8'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
hdf8 = st_transform(hdf8, crs = st_crs(6345))
hdf8 = hdf8 %>% 
  mutate(id = 1)
hSp8 = as(hdf8, 'Spatial')
hmcp958 = mcp(hSp8, percent = 95, unin='m', unout='km2')
hmcp958

#h9
hx9 = h[[9]][["x"]]
hy9 = h[[9]][["y"]]

hdf9 = data.frame(hx9,hy9)
hdf9 = st_as_sf(x=hdf9, coords=c('hx9', 'hy9'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
hdf9 = st_transform(hdf9, crs = st_crs(6345))
hdf9 = hdf9 %>% 
  mutate(id = 1)
hSp9 = as(hdf9, 'Spatial')
hmcp959 = mcp(hSp9, percent = 95, unin='m', unout='km2')
hmcp959

#h10
hx10 = h[[10]][["x"]]
hy10 = h[[10]][["y"]]

hdf10 = data.frame(hx10,hy10)
hdf10 = st_as_sf(x=hdf10, coords=c('hx10', 'hy10'), crs = "+proj=longlat +datum=NAD83 +no_defs +type=crs")
hdf10 = st_transform(hdf10, crs = st_crs(6345))
hdf10 = hdf10 %>% 
  mutate(id = 1)
hSp10 = as(hdf10, 'Spatial')
hmcp9510 = mcp(hSp10, percent = 95, unin='m', unout='km2')
hmcp9510

hmcpr = c(hmcp951, hmcp952, hmcp953, hmcp953, hmcp955, hmcp956, hmcp957, hmcp958, hmcp959, hmcp9510)
hmcpr = c(2.756813, 3.033749, 2.784158, 2.784158, 2.520014, 2.477614, 2.637883, 2.283295, 2.854224, 2.965071)


mcpmeanvlas = c(mean(amcpr), mean(bmcpr), mean(cmcpr), mean(dmcpr), mean(emcpr), mean(fmcpr), mean(gmcpr), mean(hmcpr))

amcpse = sd(amcpr)/sqrt(10)
bmcpse = sd(bmcpr)/sqrt(10)
cmcpse = sd(cmcpr)/sqrt(10)
dmcpse = sd(dmcpr)/sqrt(10)
emcpse = sd(emcpr)/sqrt(10)
fmcpse = sd(fmcpr)/sqrt(10)
gmcpse = sd(gmcpr)/sqrt(10)
hmcpse = sd(hmcpr)/sqrt(10)
semcpvals = c(amcpse, bmcpse, cmcpse, dmcpse, emcpse, fmcpse, gmcpse, hmcpse)
semcpvals

xvalsr = c(25, 50, 75, 100, 150, 200, 250, 300)
plot(xvalsr, mcpmeanvlas, ylim=c(1, 3.5))
arrows(x0=xvalsr, y0=mcpmeanvlas-semcpvals, x1=xvalsr, y1=mcpmeanvlas+semcpvals, code = 3, angle = 90, length = 0.1)

mean(amcpr)
mean(fmcpr)
mean(dmcpr)
mean(emcpr)
```

Replicates and plot for kernel density method. I ran 10 replicates and could not figure out how to get a for loop to work so I ran each one manually.
```{r}
#a1
akernelHrefEpa1 = kernelUD(aSp1, h='href', kern='epa')
aker1 = kernel.area(akernelHrefEpa1, unin = "m", unout = "km2")

#a2
akernelHrefEpa2 = kernelUD(aSp2, h='href', kern='epa')
aker2 = kernel.area(akernelHrefEpa2, unin = "m", unout = "km2")

#a3
akernelHrefEpa3 = kernelUD(aSp3, h='href', kern='epa')
aker3 = kernel.area(akernelHrefEpa3, unin = "m", unout = "km2")

#a4
akernelHrefEpa4 = kernelUD(aSp4, h='href', kern='epa')
aker4 = kernel.area(akernelHrefEpa4, unin = "m", unout = "km2")

#a5
akernelHrefEpa5 = kernelUD(aSp5, h='href', kern='epa')
aker5 = kernel.area(akernelHrefEpa5, unin = "m", unout = "km2")

#a6
akernelHrefEpa6 = kernelUD(aSp6, h='href', kern='epa')
aker6 = kernel.area(akernelHrefEpa6, unin = "m", unout = "km2")

#a7
akernelHrefEpa7 = kernelUD(aSp7, h='href', kern='epa')
aker7 = kernel.area(akernelHrefEpa7, unin = "m", unout = "km2")

#a8
akernelHrefEpa8 = kernelUD(aSp8, h='href', kern='epa')
aker8 = kernel.area(akernelHrefEpa8, unin = "m", unout = "km2")

#a9
akernelHrefEpa9 = kernelUD(aSp9, h='href', kern='epa')
aker9 = kernel.area(akernelHrefEpa9, unin = "m", unout = "km2")

#a10
akernelHrefEpa10 = kernelUD(aSp10, h='href', kern='epa')
aker10 = kernel.area(akernelHrefEpa10, unin = "m", unout = "km2")

akerr = c(aker1, aker2, aker3, aker4, aker5, aker6, aker7, aker8, aker9, aker10)
akerr = c(2.8819002, 1.4220468, 2.6577203, 2.6807532, 3.4734644, 2.2605310, 4.8124193, 1.3919010, 1.7313579, 3.1259180)

#b1
bkernelHrefEpa1 = kernelUD(bSp1, h='href', kern='epa')
bker1 = kernel.area(bkernelHrefEpa1, unin = "m", unout = "km2")

#b2
bkernelHrefEpa2 = kernelUD(bSp2, h='href', kern='epa')
bker2 = kernel.area(bkernelHrefEpa2, unin = "m", unout = "km2")

#b3
bkernelHrefEpa3 = kernelUD(bSp3, h='href', kern='epa')
bker3 = kernel.area(bkernelHrefEpa3, unin = "m", unout = "km2")

#b4
bkernelHrefEpa4 = kernelUD(bSp4, h='href', kern='epa')
bker4 = kernel.area(bkernelHrefEpa4, unin = "m", unout = "km2")

#b5
bkernelHrefEpa5 = kernelUD(bSp5, h='href', kern='epa')
bker5 = kernel.area(bkernelHrefEpa5, unin = "m", unout = "km2")

#b6
bkernelHrefEpa6 = kernelUD(bSp6, h='href', kern='epa')
bker6 = kernel.area(bkernelHrefEpa6, unin = "m", unout = "km2")

#b7
bkernelHrefEpa7 = kernelUD(bSp7, h='href', kern='epa')
bker7 = kernel.area(bkernelHrefEpa7, unin = "m", unout = "km2")

#b8
bkernelHrefEpa8 = kernelUD(bSp8, h='href', kern='epa')
bker8 = kernel.area(bkernelHrefEpa8, unin = "m", unout = "km2")

#b9
bkernelHrefEpa9 = kernelUD(bSp9, h='href', kern='epa')
bker9 = kernel.area(bkernelHrefEpa9, unin = "m", unout = "km2")

#b10
bkernelHrefEpa10 = kernelUD(bSp10, h='href', kern='epa')
bker10 = kernel.area(bkernelHrefEpa10, unin = "m", unout = "km2")

bkerr = c(bker1, bker2, bker3, bker4, bker5, bker6, bker7, bker8, bker9, bker10)
bkerr = c(2.6913911, 3.9601967, 2.6079322, 2.4551913, 3.5002131, 3.5075323, 3.1207020, 3.4192926, 2.3998027, 2.7598414)

#c1
ckernelHrefEpa1 = kernelUD(cSp1, h='href', kern='epa')
cker1 = kernel.area(ckernelHrefEpa1, unin = "m", unout = "km2")

#c2
ckernelHrefEpa2 = kernelUD(cSp2, h='href', kern='epa')
cker2 = kernel.area(ckernelHrefEpa2, unin = "m", unout = "km2")

#c3
ckernelHrefEpa3 = kernelUD(cSp3, h='href', kern='epa')
cker3 = kernel.area(ckernelHrefEpa3, unin = "m", unout = "km2")

#c4
ckernelHrefEpa4 = kernelUD(cSp4, h='href', kern='epa')
cker4 = kernel.area(ckernelHrefEpa4, unin = "m", unout = "km2")

#c5
ckernelHrefEpa5 = kernelUD(cSp5, h='href', kern='epa')
cker5 = kernel.area(ckernelHrefEpa5, unin = "m", unout = "km2")

#c6
ckernelHrefEpa6 = kernelUD(cSp6, h='href', kern='epa')
cker6 = kernel.area(ckernelHrefEpa6, unin = "m", unout = "km2")

#c7
ckernelHrefEpa7 = kernelUD(cSp7, h='href', kern='epa')
cker7 = kernel.area(ckernelHrefEpa7, unin = "m", unout = "km2")

#c8
ckernelHrefEpa8 = kernelUD(cSp8, h='href', kern='epa')
cker8 = kernel.area(ckernelHrefEpa8, unin = "m", unout = "km2")

#c9
ckernelHrefEpa9 = kernelUD(cSp9, h='href', kern='epa')
cker9 = kernel.area(ckernelHrefEpa9, unin = "m", unout = "km2")

#c10
ckernelHrefEpa10 = kernelUD(cSp10, h='href', kern='epa')
cker10 = kernel.area(ckernelHrefEpa10, unin = "m", unout = "km2")

ckerr = c(cker1, cker2, cker3, cker4, cker5, cker6, cker7, cker8, cker9, cker10)
ckerr = c(3.3200572, 2.6826920, 2.8332523, 2.3488538, 3.9625030, 2.8720662, 4.1759604, 2.8321146, 3.5076719, 3.8803465)

#d1
dkernelHrefEpa1 = kernelUD(dSp1, h='href', kern='epa')
dker1 = kernel.area(dkernelHrefEpa1, unin = "m", unout = "km2")

#d2
dkernelHrefEpa2 = kernelUD(dSp2, h='href', kern='epa')
dker2 = kernel.area(dkernelHrefEpa2, unin = "m", unout = "km2")

#d3
dkernelHrefEpa3 = kernelUD(dSp3, h='href', kern='epa')
dker3 = kernel.area(dkernelHrefEpa3, unin = "m", unout = "km2")

#d4
dkernelHrefEpa4 = kernelUD(dSp4, h='href', kern='epa')
dker4 = kernel.area(dkernelHrefEpa4, unin = "m", unout = "km2")

#d5
dkernelHrefEpa5 = kernelUD(dSp5, h='href', kern='epa')
dker5 = kernel.area(dkernelHrefEpa5, unin = "m", unout = "km2")

#d6
dkernelHrefEpa6 = kernelUD(dSp6, h='href', kern='epa')
dker6 = kernel.area(dkernelHrefEpa6, unin = "m", unout = "km2")

#d7
dkernelHrefEpa7 = kernelUD(dSp7, h='href', kern='epa')
dker7 = kernel.area(dkernelHrefEpa7, unin = "m", unout = "km2")

#d8
dkernelHrefEpa8 = kernelUD(dSp8, h='href', kern='epa')
dker8 = kernel.area(dkernelHrefEpa8, unin = "m", unout = "km2")

#d9
dkernelHrefEpa9 = kernelUD(dSp9, h='href', kern='epa')
dker9 = kernel.area(dkernelHrefEpa9, unin = "m", unout = "km2")

#d10
dkernelHrefEpa10 = kernelUD(dSp10, h='href', kern='epa')
dker10 = kernel.area(dkernelHrefEpa10, unin = "m", unout = "km2")

dkerr = c(dker1, dker2, dker3, dker4, dker5, dker6, dker7, dker8, dker9, dker10)
dkerr = c(3.3639520, 2.9692828, 3.6744953, 3.6319283, 3.9499692, 2.9275158, 3.8757002, 2.9854132, 2.8047696, 3.5655089)

#e1
ekernelHrefEpa1 = kernelUD(eSp1, h='href', kern='epa')
eker1 = kernel.area(ekernelHrefEpa1, unin = "m", unout = "km2")

#e2
ekernelHrefEpa2 = kernelUD(eSp2, h='href', kern='epa')
eker2 = kernel.area(ekernelHrefEpa2, unin = "m", unout = "km2")

#e3
ekernelHrefEpa3 = kernelUD(eSp3, h='href', kern='epa')
eker3 = kernel.area(ekernelHrefEpa3, unin = "m", unout = "km2")

#e4
ekernelHrefEpa4 = kernelUD(eSp4, h='href', kern='epa')
eker4 = kernel.area(ekernelHrefEpa4, unin = "m", unout = "km2")

#e5
ekernelHrefEpa5 = kernelUD(eSp5, h='href', kern='epa')
eker5 = kernel.area(ekernelHrefEpa5, unin = "m", unout = "km2")

#e6
ekernelHrefEpa6 = kernelUD(eSp6, h='href', kern='epa')
eker6 = kernel.area(ekernelHrefEpa6, unin = "m", unout = "km2")

#e7
ekernelHrefEpa7 = kernelUD(eSp7, h='href', kern='epa')
eker7 = kernel.area(ekernelHrefEpa7, unin = "m", unout = "km2")

#e8
ekernelHrefEpa8 = kernelUD(eSp8, h='href', kern='epa')
eker8 = kernel.area(ekernelHrefEpa8, unin = "m", unout = "km2")

#e9
ekernelHrefEpa9 = kernelUD(eSp9, h='href', kern='epa')
eker9 = kernel.area(ekernelHrefEpa9, unin = "m", unout = "km2")

#e10
ekernelHrefEpa10 = kernelUD(eSp10, h='href', kern='epa')
eker10 = kernel.area(ekernelHrefEpa10, unin = "m", unout = "km2")

ekerr = c(eker1, eker2, eker3, eker4, eker5, eker6, eker7, eker8, eker9, eker10)
ekerr = c(2.7341022, 3.8148132, 3.3070227, 2.9550158, 3.3971322, 3.1948494, 3.1646877, 2.8083924, 3.8718249, 3.0617832)

#f1
fkernelHrefEpa1 = kernelUD(fSp1, h='href', kern='epa')
fker1 = kernel.area(fkernelHrefEpa1, unin = "m", unout = "km2")

#f2
fkernelHrefEpa2 = kernelUD(fSp2, h='href', kern='epa')
fker2 = kernel.area(fkernelHrefEpa2, unin = "m", unout = "km2")

#f3
fkernelHrefEpa3 = kernelUD(fSp3, h='href', kern='epa')
fker3 = kernel.area(fkernelHrefEpa3, unin = "m", unout = "km2")

#f4
fkernelHrefEpa4 = kernelUD(fSp4, h='href', kern='epa')
fker4 = kernel.area(fkernelHrefEpa4, unin = "m", unout = "km2")

#f5
fkernelHrefEpa5 = kernelUD(fSp5, h='href', kern='epa')
fker5 = kernel.area(fkernelHrefEpa5, unin = "m", unout = "km2")

#f6
fkernelHrefEpa6 = kernelUD(fSp6, h='href', kern='epa')
fker6 = kernel.area(fkernelHrefEpa6, unin = "m", unout = "km2")

#f7
fkernelHrefEpa7 = kernelUD(fSp7, h='href', kern='epa')
fker7 = kernel.area(fkernelHrefEpa7, unin = "m", unout = "km2")

#f8
fkernelHrefEpa8 = kernelUD(fSp8, h='href', kern='epa')
fker8 = kernel.area(fkernelHrefEpa8, unin = "m", unout = "km2")

#f9
fkernelHrefEpa9 = kernelUD(fSp9, h='href', kern='epa')
fker9 = kernel.area(fkernelHrefEpa9, unin = "m", unout = "km2")

#f10
fkernelHrefEpa10 = kernelUD(fSp10, h='href', kern='epa')
fker10 = kernel.area(fkernelHrefEpa10, unin = "m", unout = "km2")

fkerr = c(fker1, fker2, fker3, fker4, fker5, fker6, fker7, fker8, fker9, fker10)
fkerr = c(3.1825345, 4.0660612, 3.9003211, 3.5278959, 3.8037414, 3.1504651, 3.8054025, 3.1622618, 3.7931163, 2.9982938)

#g1
gkernelHrefEpa1 = kernelUD(gSp1, h='href', kern='epa')
gker1 = kernel.area(gkernelHrefEpa1, unin = "m", unout = "km2")

#g2
gkernelHrefEpa2 = kernelUD(gSp2, h='href', kern='epa')
gker2 = kernel.area(gkernelHrefEpa2, unin = "m", unout = "km2")

#g3
gkernelHrefEpa3 = kernelUD(gSp3, h='href', kern='epa')
gker3 = kernel.area(gkernelHrefEpa3, unin = "m", unout = "km2")

#g4
gkernelHrefEpa4 = kernelUD(gSp4, h='href', kern='epa')
gker4 = kernel.area(gkernelHrefEpa4, unin = "m", unout = "km2")

#g5
gkernelHrefEpa5 = kernelUD(gSp5, h='href', kern='epa')
gker5 = kernel.area(gkernelHrefEpa5, unin = "m", unout = "km2")

#g6
gkernelHrefEpa6 = kernelUD(gSp6, h='href', kern='epa')
gker6 = kernel.area(gkernelHrefEpa6, unin = "m", unout = "km2")

#g7
gkernelHrefEpa7 = kernelUD(gSp7, h='href', kern='epa')
gker7 = kernel.area(gkernelHrefEpa7, unin = "m", unout = "km2")

#g8
gkernelHrefEpa8 = kernelUD(gSp8, h='href', kern='epa')
gker8 = kernel.area(gkernelHrefEpa8, unin = "m", unout = "km2")

#g9
gkernelHrefEpa9 = kernelUD(gSp9, h='href', kern='epa')
gker9 = kernel.area(gkernelHrefEpa9, unin = "m", unout = "km2")

#g10
gkernelHrefEpa10 = kernelUD(gSp10, h='href', kern='epa')
gker10 = kernel.area(gkernelHrefEpa10, unin = "m", unout = "km2")

gkerr = c(gker1, gker2, gker3, gker4, gker5, gker6, gker7, gker8, gker9, gker10)
gkerr = c(3.2626258, 3.6148884, 3.3471369, 3.5739246, 3.3571861, 3.3233439, 3.8426721, 3.1708048, 4.0312471, 3.2886415)

#h1
hkernelHrefEpa1 = kernelUD(hSp1, h='href', kern='epa')
hker1 = kernel.area(hkernelHrefEpa1, unin = "m", unout = "km2")

#h2
hkernelHrefEpa2 = kernelUD(hSp2, h='href', kern='epa')
hker2 = kernel.area(hkernelHrefEpa2, unin = "m", unout = "km2")


#h3
hkernelHrefEpa3 = kernelUD(hSp3, h='href', kern='epa')
hker3 = kernel.area(hkernelHrefEpa3, unin = "m", unout = "km2")

#h4
hkernelHrefEpa4 = kernelUD(hSp4, h='href', kern='epa')
hker4 = kernel.area(hkernelHrefEpa4, unin = "m", unout = "km2")

#h5
hkernelHrefEpa5 = kernelUD(hSp5, h='href', kern='epa')
hker5 = kernel.area(hkernelHrefEpa5, unin = "m", unout = "km2")

#h6
hkernelHrefEpa6 = kernelUD(hSp6, h='href', kern='epa')
hker6 = kernel.area(hkernelHrefEpa6, unin = "m", unout = "km2")

#h7
hkernelHrefEpa7 = kernelUD(hSp7, h='href', kern='epa')
hker7 = kernel.area(hkernelHrefEpa7, unin = "m", unout = "km2")

#h8
hkernelHrefEpa8 = kernelUD(hSp8, h='href', kern='epa')
hker8 = kernel.area(hkernelHrefEpa8, unin = "m", unout = "km2")

#h9
hkernelHrefEpa9 = kernelUD(hSp9, h='href', kern='epa')
hker9 = kernel.area(hkernelHrefEpa9, unin = "m", unout = "km2")

#h10
hkernelHrefEpa10 = kernelUD(hSp10, h='href', kern='epa')
hker10 = kernel.area(hkernelHrefEpa10, unin = "m", unout = "km2")

hkerr = c(hker1, hker2, hker3, hker4, hker5, hker6, hker7, hker8, hker9, hker10)
hkerr = c(3.5436085, 3.7327635, 3.4910436, 3.3613031, 3.0680060, 3.1827357, 3.4217309, 3.1193420, 3.6878728, 3.6223772)

kerrmeanvlas = c(mean(akerr), mean(bkerr), mean(ckerr), mean(dkerr), mean(ekerr), mean(fkerr), mean(gkerr), mean(hkerr))

akerse = sd(akerr)/sqrt(10)
bkerse = sd(bkerr)/sqrt(10)
ckerse = sd(ckerr)/sqrt(10)
dkerse = sd(dkerr)/sqrt(10)
ekerse = sd(ekerr)/sqrt(10)
fkerse = sd(fkerr)/sqrt(10)
gkerse = sd(gkerr)/sqrt(10)
hkerse = sd(hkerr)/sqrt(10)
sekervals = c(akerse, bkerse, ckerse, dkerse, ekerse, fkerse, gkerse, hkerse)

plot(xvalsr, kerrmeanvlas, ylim=c(2.0, 4.0))
arrows(x0=xvalsr, y0=kerrmeanvlas-sekervals, x1=xvalsr, y1=kerrmeanvlas+sekervals, code = 3, angle = 90, length = 0.1)

mean(akerr)
mean(fkerr)
mean(dkerr)
```

Replicates and estimates using the local convex hull (a-locoh) method. I only ran 5 replicates of each simulated number of points because of how long it took the code to run. Because each time I ran the code I needed to use a different value of "a", using a for loop would not have worked for the local convex hull method. NOTE: This section of code takes a very long time to run
```{r}
#a-LoCoH
#a1
aaInit1 = round(max(dist(coordinates(aSp1))),0)
aaSearch1 = seq(aaInit1, 2*aaInit1, by=100)
alocohArange1 = LoCoH.a.area(SpatialPoints(coordinates(aSp1)), arange=aaSearch1)
alocohA1 = LoCoH.a(SpatialPoints(coordinates(aSp1)), a=aaSearch1[8], unin = "m", unout = "km2")
alocohASf1 = st_as_sf(alocohA1)
alocohA92Sf1 = alocohASf1[22,]
alocohA92Sf1

#a2
aaInit2 = round(max(dist(coordinates(aSp2))),0)
aaSearch2 = seq(aaInit2, 2*aaInit2, by=100)
alocohArange2 = LoCoH.a.area(SpatialPoints(coordinates(aSp2)), arange=aaSearch2)
alocohA2 = LoCoH.a(SpatialPoints(coordinates(aSp2)), a=aaSearch2[12], unin = "m", unout = "km2")
alocohASf2 = st_as_sf(alocohA2)
alocohA96Sf2 = alocohASf2[16,]
alocohA96Sf2

#a3
aaInit3 = round(max(dist(coordinates(aSp3))),0)
aaSearch3 = seq(aaInit3, 2*aaInit3, by=100)
alocohArange3 = LoCoH.a.area(SpatialPoints(coordinates(aSp3)), arange=aaSearch3)
alocohA3 = LoCoH.a(SpatialPoints(coordinates(aSp3)), a=aaSearch3[7], unin = "m", unout = "km2")
alocohASf3 = st_as_sf(alocohA3)
alocohA100Sf3 = alocohASf3[23,]
alocohA100Sf3

#a4
aaInit4 = round(max(dist(coordinates(aSp4))),0)
aaSearch4 = seq(aaInit4, 2*aaInit4, by=100)
alocohArange4 = LoCoH.a.area(SpatialPoints(coordinates(aSp4)), arange=aaSearch4)
alocohA4 = LoCoH.a(SpatialPoints(coordinates(aSp4)), a=aaSearch4[16], unin = "m", unout = "km2")
alocohASf4 = st_as_sf(alocohA4)
alocohA96Sf4 = alocohASf4[16,]
alocohA96Sf4

#a5
aaInit5 = round(max(dist(coordinates(aSp5))),0)
aaSearch5 = seq(aaInit5, 2*aaInit5, by=100)
alocohArange5 = LoCoH.a.area(SpatialPoints(coordinates(aSp5)), arange=aaSearch5)
alocohA5 = LoCoH.a(SpatialPoints(coordinates(aSp5)), a=aaSearch5[17], unin = "m", unout = "km2")
alocohASf5 = st_as_sf(alocohA5)
alocohA96Sf5 = alocohASf5[22,]
alocohA96Sf5

#a6
aaInit6 = round(max(dist(coordinates(aSp6))),0)
aaSearch6 = seq(aaInit6, 2*aaInit6, by=100)
alocohArange6 = LoCoH.a.area(SpatialPoints(coordinates(aSp6)), arange=aaSearch6)
alocohA6 = LoCoH.a(SpatialPoints(coordinates(aSp6)), a=aaSearch6[8], unin = "m", unout = "km2")
alocohASf6 = st_as_sf(alocohA6)
alocohA96Sf6 = alocohASf6[14,]
alocohA96Sf6

#a7
aaInit7 = round(max(dist(coordinates(aSp7))),0)
aaSearch7 = seq(aaInit7, 2*aaInit7, by=100)
alocohArange7 = LoCoH.a.area(SpatialPoints(coordinates(aSp7)), arange=aaSearch7)
alocohA7 = LoCoH.a(SpatialPoints(coordinates(aSp7)), a=aaSearch7[12], unin = "m", unout = "km2")
alocohASf7 = st_as_sf(alocohA7)
alocohA96Sf7 = alocohASf7[19,]
alocohA96Sf7

#a8
aaInit8 = round(max(dist(coordinates(aSp8))),0)
aaSearch8 = seq(aaInit8, 2*aaInit8, by=100)
alocohArange8 = LoCoH.a.area(SpatialPoints(coordinates(aSp8)), arange=aaSearch8)
alocohA8 = LoCoH.a(SpatialPoints(coordinates(aSp8)), a=aaSearch8[10], unin = "m", unout = "km2")
alocohASf8 = st_as_sf(alocohA8)
alocohA96Sf8 = alocohASf8[17,]
alocohA96Sf8

#a9
aaInit9 = round(max(dist(coordinates(aSp9))),0)
aaSearch9 = seq(aaInit9, 2*aaInit9, by=100)
alocohArange9 = LoCoH.a.area(SpatialPoints(coordinates(aSp9)), arange=aaSearch9)
alocohA9 = LoCoH.a(SpatialPoints(coordinates(aSp9)), a=aaSearch9[11], unin = "m", unout = "km2")
alocohASf9 = st_as_sf(alocohA9)
alocohA96Sf9 = alocohASf9[13,]
alocohA96Sf9

#a10
aaInit10 = round(max(dist(coordinates(aSp10))),0)
aaSearch10 = seq(aaInit10, 2*aaInit10, by=100)
alocohArange10 = LoCoH.a.area(SpatialPoints(coordinates(aSp10)), arange=aaSearch10)
alocohA10 = LoCoH.a(SpatialPoints(coordinates(aSp10)), a=aaSearch10[22], unin = "m", unout = "km2")
alocohASf10 = st_as_sf(alocohA10)
alocohA100Sf10 = alocohASf10[20,]
alocohA100Sf10

alocoh = c(alocohA92Sf1, alocohA96Sf2, alocohA100Sf3, alocohA96Sf4, alocohA96Sf5)
alocoh = c(1.008646, 0.5731333, 1.293166, 1.159358, 1.252994)

#b1
baInit1 = round(max(dist(coordinates(bSp1))),0)
baSearch1 = seq(baInit1, 2*baInit1, by=100)
blocohArange1 = LoCoH.a.area(SpatialPoints(coordinates(bSp1)), arange=baSearch1)
blocohA1 = LoCoH.a(SpatialPoints(coordinates(bSp1)), a=baSearch1[14], unin = "m", unout = "km2")
blocohASf1 = st_as_sf(blocohA1)
blocohA96Sf1 = blocohASf1[40,]
blocohA96Sf1

#b2
baInit2 = round(max(dist(coordinates(bSp2))),0)
baSearch2 = seq(baInit2, 2*baInit2, by=100)
blocohArange2 = LoCoH.a.area(SpatialPoints(coordinates(bSp2)), arange=baSearch2)
blocohA2 = LoCoH.a(SpatialPoints(coordinates(bSp2)), a=baSearch2[27], unin = "m", unout = "km2")
blocohASf2 = st_as_sf(blocohA2)
blocohA96Sf2 = blocohASf2[43,]
blocohA96Sf2

#b3
baInit3 = round(max(dist(coordinates(bSp3))),0)
baSearch3 = seq(baInit3, 2*baInit3, by=100)
blocohArange3 = LoCoH.a.area(SpatialPoints(coordinates(bSp3)), arange=baSearch3)
blocohA3 = LoCoH.a(SpatialPoints(coordinates(bSp3)), a=baSearch3[7], unin = "m", unout = "km2")
blocohASf3 = st_as_sf(blocohA3)
blocohA96Sf3 = blocohASf3[39,]
blocohA96Sf3

#b4
baInit4 = round(max(dist(coordinates(bSp4))),0)
baSearch4 = seq(baInit4, 2*baInit4, by=100)
blocohArange4 = LoCoH.a.area(SpatialPoints(coordinates(bSp4)), arange=baSearch4)
blocohA4 = LoCoH.a(SpatialPoints(coordinates(bSp4)), a=baSearch4[11], unin = "m", unout = "km2")
blocohASf4 = st_as_sf(blocohA4)
blocohA96Sf4 = blocohASf4[43,]
blocohA96Sf4

#b5
baInit5 = round(max(dist(coordinates(bSp5))),0)
baSearch5 = seq(baInit5, 2*baInit5, by=100)
blocohArange5 = LoCoH.a.area(SpatialPoints(coordinates(bSp5)), arange=baSearch5)
blocohA5 = LoCoH.a(SpatialPoints(coordinates(bSp5)), a=baSearch5[12], unin = "m", unout = "km2")
blocohASf5 = st_as_sf(blocohA5)
blocohA96Sf5 = blocohASf5[37,]
blocohA96Sf5

blocoh = c(blocohA96Sf1, blocohA96Sf2, blocohA96Sf3, blocohA96Sf4, blocohA96Sf5)
blocoh = c(1.373954, 2.097635, 1.236619, 1.171671, 1.699471)

#c1
caInit1 = round(max(dist(coordinates(cSp1))),0)
caSearch1 = seq(caInit1, 2*caInit1, by=100)
clocohArange1 = LoCoH.a.area(SpatialPoints(coordinates(cSp1)), arange=caSearch1)
clocohA1 = LoCoH.a(SpatialPoints(coordinates(cSp1)), a=caSearch1[16], unin = "m", unout = "km2")
clocohASf1 = st_as_sf(clocohA1)
clocohA95Sf1 = clocohASf1[63,]
clocohA95Sf1

#c2
caInit2 = round(max(dist(coordinates(cSp2))),0)
caSearch2 = seq(caInit2, 2*caInit2, by=100)
clocohArange2 = LoCoH.a.area(SpatialPoints(coordinates(cSp2)), arange=caSearch2)
clocohA2 = LoCoH.a(SpatialPoints(coordinates(cSp2)), a=caSearch2[16], unin = "m", unout = "km2")
clocohASf2 = st_as_sf(clocohA2)
clocohA95Sf2 = clocohASf2[56,]
clocohA95Sf2

#c3
caInit3 = round(max(dist(coordinates(cSp3))),0)
caSearch3 = seq(caInit3, 2*caInit3, by=100)
clocohArange3 = LoCoH.a.area(SpatialPoints(coordinates(cSp3)), arange=caSearch3)
clocohA3 = LoCoH.a(SpatialPoints(coordinates(cSp3)), a=caSearch3[9], unin = "m", unout = "km2")
clocohASf3 = st_as_sf(clocohA3)
clocohA96Sf3 = clocohASf3[68,]
clocohA96Sf3

#c4
caInit4 = round(max(dist(coordinates(cSp4))),0)
caSearch4 = seq(caInit4, 2*caInit4, by=100)
clocohArange4 = LoCoH.a.area(SpatialPoints(coordinates(cSp4)), arange=caSearch4)
clocohA4 = LoCoH.a(SpatialPoints(coordinates(cSp4)), a=caSearch4[20], unin = "m", unout = "km2")
clocohASf4 = st_as_sf(clocohA4)
clocohA95Sf4 = clocohASf4[54,]
clocohA95Sf4

#c5
caInit5 = round(max(dist(coordinates(cSp5))),0)
caSearch5 = seq(caInit5, 2*caInit5, by=100)
clocohArange5 = LoCoH.a.area(SpatialPoints(coordinates(cSp5)), arange=caSearch5)
clocohA5 = LoCoH.a(SpatialPoints(coordinates(cSp5)), a=caSearch5[24], unin = "m", unout = "km2")
clocohASf5 = st_as_sf(clocohA5)
clocohA95Sf5 = clocohASf5[57,]
clocohA95Sf5

clocoh = c(clocohA95Sf1, clocohA95Sf2, clocohA96Sf3, clocohA95Sf4, clocohA95Sf5)
clocoh = c(1.836921, 1.355225, 1.580981, 1.25825, 2.195709)

#d1
daInit1 = round(max(dist(coordinates(dSp1))),0)
daSearch1 = seq(daInit1, 2*daInit1, by=100)
dlocohArange1 = LoCoH.a.area(SpatialPoints(coordinates(dSp1)), arange=daSearch1)
dlocohA1 = LoCoH.a(SpatialPoints(coordinates(dSp1)), a=daSearch1[26], unin = "m", unout = "km2")
dlocohASf1 = st_as_sf(dlocohA1)
dlocohA95Sf1 = dlocohASf1[74,]
dlocohA95Sf1

#d2
daInit2 = round(max(dist(coordinates(dSp2))),0)
daSearch2 = seq(daInit2, 2*daInit2, by=100)
dlocohArange2 = LoCoH.a.area(SpatialPoints(coordinates(dSp2)), arange=daSearch2)
dlocohA2 = LoCoH.a(SpatialPoints(coordinates(dSp2)), a=daSearch2[19], unin = "m", unout = "km2")
dlocohASf2 = st_as_sf(dlocohA2)
dlocohA95Sf2 = dlocohASf2[80,]
dlocohA95Sf2

#d3
daInit3 = round(max(dist(coordinates(dSp3))),0)
daSearch3 = seq(daInit3, 2*daInit3, by=100)
dlocohArange3 = LoCoH.a.area(SpatialPoints(coordinates(dSp3)), arange=daSearch3)
dlocohA3 = LoCoH.a(SpatialPoints(coordinates(dSp3)), a=daSearch3[12], unin = "m", unout = "km2")
dlocohASf3 = st_as_sf(dlocohA3)
dlocohA95Sf3 = dlocohASf3[80,]
dlocohA95Sf3

#d4
daInit4 = round(max(dist(coordinates(dSp4))),0)
daSearch4 = seq(daInit4, 2*daInit4, by=100)
dlocohArange4 = LoCoH.a.area(SpatialPoints(coordinates(dSp4)), arange=daSearch4)
dlocohA4 = LoCoH.a(SpatialPoints(coordinates(dSp4)), a=daSearch4[16], unin = "m", unout = "km2")
dlocohASf4 = st_as_sf(dlocohA4)
dlocohA95Sf4 = dlocohASf4[80,]
dlocohA95Sf4

#d5
daInit5 = round(max(dist(coordinates(dSp5))),0)
daSearch5 = seq(daInit5, 2*daInit5, by=100)
dlocohArange5 = LoCoH.a.area(SpatialPoints(coordinates(dSp5)), arange=daSearch5)
dlocohA5 = LoCoH.a(SpatialPoints(coordinates(dSp5)), a=daSearch5[22], unin = "m", unout = "km2")
dlocohASf5 = st_as_sf(dlocohA5)
dlocohA95Sf5 = dlocohASf5[83,]
dlocohA95Sf5

dlocoh = c(dlocohA95Sf1, dlocohA95Sf2, dlocohA95Sf3, dlocohA95Sf4, dlocohA95Sf5)
dlocoh = c(1.987829, 1.869688, 2.227091, 2.100333, 2.328297)

#e1
eaInit1 = round(max(dist(coordinates(eSp1))),0)
eaSearch1 = seq(eaInit1, 2*eaInit1, by=100)
elocohArange1 = LoCoH.a.area(SpatialPoints(coordinates(eSp1)), arange=eaSearch1)
elocohA1 = LoCoH.a(SpatialPoints(coordinates(eSp1)), a=eaSearch1[11], unin = "m", unout = "km2")
elocohASf1 = st_as_sf(elocohA1)
elocohA95Sf1 = elocohASf1[125,]
elocohA95Sf1

#e2
eaInit2 = round(max(dist(coordinates(eSp2))),0)
eaSearch2 = seq(eaInit2, 2*eaInit2, by=100)
elocohArange2 = LoCoH.a.area(SpatialPoints(coordinates(eSp2)), arange=eaSearch2)
elocohA2 = LoCoH.a(SpatialPoints(coordinates(eSp2)), a=eaSearch2[17], unin = "m", unout = "km2")
elocohASf2 = st_as_sf(elocohA2)
elocohA95Sf2 = elocohASf2[123,]
elocohA95Sf2

#e3
eaInit3 = round(max(dist(coordinates(eSp3))),0)
eaSearch3 = seq(eaInit3, 2*eaInit3, by=100)
elocohArange3 = LoCoH.a.area(SpatialPoints(coordinates(eSp3)), arange=eaSearch3)
elocohA3 = LoCoH.a(SpatialPoints(coordinates(eSp3)), a=eaSearch3[23], unin = "m", unout = "km2")
elocohASf3 = st_as_sf(elocohA3)
elocohA95Sf3 = elocohASf3[125,]
elocohA95Sf3

#e4
eaInit4 = round(max(dist(coordinates(eSp4))),0)
eaSearch4 = seq(eaInit4, 2*eaInit4, by=100)
elocohArange4 = LoCoH.a.area(SpatialPoints(coordinates(eSp4)), arange=eaSearch4)
elocohA4 = LoCoH.a(SpatialPoints(coordinates(eSp4)), a=eaSearch4[21], unin = "m", unout = "km2")
elocohASf4 = st_as_sf(elocohA4)
elocohA95Sf4 = elocohASf4[113,]
elocohA95Sf4

#e5
eaInit5 = round(max(dist(coordinates(eSp5))),0)
eaSearch5 = seq(eaInit5, 2*eaInit5, by=100)
elocohArange5 = LoCoH.a.area(SpatialPoints(coordinates(eSp5)), arange=eaSearch5)
elocohA5 = LoCoH.a(SpatialPoints(coordinates(eSp5)), a=eaSearch5[10], unin = "m", unout = "km2")
elocohASf5 = st_as_sf(elocohA5)
elocohA95Sf5 = elocohASf5[116,]
elocohA95Sf5

elocoh = c(elocohA95Sf1, elocohA95Sf2, elocohA95Sf3, elocohA95Sf4, elocohA95Sf5)
elocoh = c(1.733512, 2.358944, 2.205587, 1.935492, 2.121135)

#f1
faInit1 = round(max(dist(coordinates(fSp1))),0)
faSearch1 = seq(faInit1, 2*faInit1, by=100)
flocohArange1 = LoCoH.a.area(SpatialPoints(coordinates(fSp1)), arange=faSearch1)
flocohA1 = LoCoH.a(SpatialPoints(coordinates(fSp1)), a=faSearch1[20], unin = "m", unout = "km2")
flocohASf1 = st_as_sf(flocohA1)
flocohA95Sf1 = flocohASf1[158,]
flocohA95Sf1

#f2
faInit2 = round(max(dist(coordinates(fSp2))),0)
faSearch2 = seq(faInit2, 2*faInit2, by=100)
flocohArange2 = LoCoH.a.area(SpatialPoints(coordinates(fSp2)), arange=faSearch2)
flocohA2 = LoCoH.a(SpatialPoints(coordinates(fSp2)), a=faSearch2[20], unin = "m", unout = "km2")
flocohASf2 = st_as_sf(flocohA2)
flocohA95Sf2 = flocohASf2[169,]
flocohA95Sf2

#f3
faInit3 = round(max(dist(coordinates(fSp3))),0)
faSearch3 = seq(faInit3, 2*faInit3, by=100)
flocohArange3 = LoCoH.a.area(SpatialPoints(coordinates(fSp3)), arange=faSearch3)
flocohA3 = LoCoH.a(SpatialPoints(coordinates(fSp3)), a=faSearch3[26], unin = "m", unout = "km2")
flocohASf3 = st_as_sf(flocohA3)
flocohA95Sf3 = flocohASf3[157,]
flocohA95Sf3

#f4
faInit4 = round(max(dist(coordinates(fSp4))),0)
faSearch4 = seq(faInit4, 2*faInit4, by=100)
flocohArange4 = LoCoH.a.area(SpatialPoints(coordinates(fSp4)), arange=faSearch4)
flocohA4 = LoCoH.a(SpatialPoints(coordinates(fSp4)), a=faSearch4[19], unin = "m", unout = "km2")
flocohASf4 = st_as_sf(flocohA4)
flocohA95Sf4 = flocohASf4[168,]
flocohA95Sf4

#f5
faInit5 = round(max(dist(coordinates(fSp5))),0)
faSearch5 = seq(faInit5, 2*faInit5, by=100)
flocohArange5 = LoCoH.a.area(SpatialPoints(coordinates(fSp5)), arange=faSearch5)
flocohA5 = LoCoH.a(SpatialPoints(coordinates(fSp5)), a=faSearch5[17], unin = "m", unout = "km2")
flocohASf5 = st_as_sf(flocohA5)
flocohA95Sf5 = flocohASf5[170,]
flocohA95Sf5

flocoh = c(flocohA95Sf1, flocohA95Sf2, flocohA95Sf3, flocohA95Sf4, flocohA95Sf5)
flocoh = c(2.2285, 2.773425, 2.731065, 2.25922, 2.634711)

#g1
gaInit1 = round(max(dist(coordinates(gSp1))),0)
gaSearch1 = seq(gaInit1, 2*gaInit1, by=100)
glocohArange1 = LoCoH.a.area(SpatialPoints(coordinates(gSp1)), arange=gaSearch1)
glocohA1 = LoCoH.a(SpatialPoints(coordinates(gSp1)), a=gaSearch1[21], unin = "m", unout = "km2")
glocohASf1 = st_as_sf(glocohA1)
glocohA95Sf1 = glocohASf1[209,]
glocohA95Sf1

#g2
gaInit2 = round(max(dist(coordinates(gSp2))),0)
gaSearch2 = seq(gaInit2, 2*gaInit2, by=100)
glocohArange2 = LoCoH.a.area(SpatialPoints(coordinates(gSp2)), arange=gaSearch2)
glocohA2 = LoCoH.a(SpatialPoints(coordinates(gSp2)), a=gaSearch2[24], unin = "m", unout = "km2")
glocohASf2 = st_as_sf(glocohA2)
glocohA95Sf2 = glocohASf2[197,]
glocohA95Sf2

#g3
gaInit3 = round(max(dist(coordinates(gSp3))),0)
gaSearch3 = seq(gaInit3, 2*gaInit3, by=100)
glocohArange3 = LoCoH.a.area(SpatialPoints(coordinates(gSp3)), arange=gaSearch3)
glocohA3 = LoCoH.a(SpatialPoints(coordinates(gSp3)), a=gaSearch3[21], unin = "m", unout = "km2")
glocohASf3 = st_as_sf(glocohA3)
glocohA95Sf3 = glocohASf3[207,]
glocohA95Sf3

#g4
gaInit4 = round(max(dist(coordinates(gSp4))),0)
gaSearch4 = seq(gaInit4, 2*gaInit4, by=100)
glocohArange4 = LoCoH.a.area(SpatialPoints(coordinates(gSp4)), arange=gaSearch4)
glocohA4 = LoCoH.a(SpatialPoints(coordinates(gSp4)), a=gaSearch4[21], unin = "m", unout = "km2")
glocohASf4 = st_as_sf(glocohA4)
glocohA95Sf4 = glocohASf4[210,]
glocohA95Sf4

#g5
gaInit5 = round(max(dist(coordinates(gSp5))),0)
gaSearch5 = seq(gaInit5, 2*gaInit5, by=100)
glocohArange5 = LoCoH.a.area(SpatialPoints(coordinates(gSp5)), arange=gaSearch5)
glocohA5 = LoCoH.a(SpatialPoints(coordinates(gSp5)), a=gaSearch5[18], unin = "m", unout = "km2")
glocohASf5 = st_as_sf(glocohA5)
glocohA95Sf5 = glocohASf5[214,]
glocohA95Sf5

glocoh = c(glocohA95Sf1, glocohA95Sf2, glocohA95Sf3, glocohA95Sf4, glocohA95Sf5)
glocoh = c(2.287755, 2.51144, 2.329861, 2.667579, 2.439136)

#h1
haInit1 = round(max(dist(coordinates(hSp1))),0)
haSearch1 = seq(haInit1, 2*haInit1, by=100)
hlocohArange1 = LoCoH.a.area(SpatialPoints(coordinates(hSp1)), arange=haSearch1)
hlocohA1 = LoCoH.a(SpatialPoints(coordinates(hSp1)), a=haSearch1[26], unin = "m", unout = "km2")
hlocohASf1 = st_as_sf(hlocohA1)
hlocohA95Sf1 = hlocohASf1[242,]
hlocohA95Sf1

#h2
haInit2 = round(max(dist(coordinates(hSp2))),0)
haSearch2 = seq(haInit2, 2*haInit2, by=100)
hlocohArange2 = LoCoH.a.area(SpatialPoints(coordinates(hSp2)), arange=haSearch2)
hlocohA2 = LoCoH.a(SpatialPoints(coordinates(hSp2)), a=haSearch2[25], unin = "m", unout = "km2")
hlocohASf2 = st_as_sf(hlocohA2)
hlocohA95Sf2 = hlocohASf2[249,]
hlocohA95Sf2

#h3
haInit3 = round(max(dist(coordinates(hSp3))),0)
haSearch3 = seq(haInit3, 2*haInit3, by=100)
hlocohArange3 = LoCoH.a.area(SpatialPoints(coordinates(hSp3)), arange=haSearch3)
hlocohA3 = LoCoH.a(SpatialPoints(coordinates(hSp3)), a=haSearch3[17], unin = "m", unout = "km2")
hlocohASf3 = st_as_sf(hlocohA3)
hlocohA95Sf3 = hlocohASf3[251,]
hlocohA95Sf3

#h4
haInit4 = round(max(dist(coordinates(hSp4))),0)
haSearch4 = seq(haInit4, 2*haInit4, by=100)
hlocohArange4 = LoCoH.a.area(SpatialPoints(coordinates(hSp4)), arange=haSearch4)
hlocohA4 = LoCoH.a(SpatialPoints(coordinates(hSp4)), a=haSearch4[11], unin = "m", unout = "km2")
hlocohASf4 = st_as_sf(hlocohA4)
hlocohA95Sf4 = hlocohASf4[249,]
hlocohA95Sf4

#h5
haInit5 = round(max(dist(coordinates(hSp5))),0)
haSearch5 = seq(haInit5, 2*haInit5, by=100)
hlocohArange5 = LoCoH.a.area(SpatialPoints(coordinates(hSp5)), arange=haSearch5)
hlocohA5 = LoCoH.a(SpatialPoints(coordinates(hSp5)), a=haSearch5[24], unin = "m", unout = "km2")
hlocohASf5 = st_as_sf(hlocohA5)
hlocohA95Sf5 = hlocohASf5[241,]
hlocohA95Sf5

hlocoh = c(hlocohA95Sf1, hlocohA95Sf2, hlocohA95Sf3, hlocohA95Sf4, hlocohA95Sf5)
hlocoh = c(2.638281, 2.710311, 2.515772, 2.35954, 2.138452)

locohmeanvlas = c(mean(alocoh), mean(blocoh), mean(clocoh), mean(dlocoh), mean(elocoh), mean(flocoh), mean(glocoh), mean(hlocoh))

alocohse = sd(alocoh)/sqrt(5)
blocohse = sd(blocoh)/sqrt(5)
clocohse = sd(clocoh)/sqrt(5)
dlocohse = sd(dlocoh)/sqrt(5)
elocohse = sd(elocoh)/sqrt(5)
flocohse = sd(flocoh)/sqrt(5)
glocohse = sd(glocoh)/sqrt(5)
hlocohse = sd(hlocoh)/sqrt(5)
selocohvals = c(alocohse, blocohse, clocohse, dlocohse, elocohse, flocohse, glocohse, hlocohse)

plot(xvalsr, locohmeanvlas, ylim=c(0.75, 3.25))
arrows(x0=xvalsr, y0=locohmeanvlas-selocohvals, x1=xvalsr, y1=locohmeanvlas+selocohvals, code = 3, angle = 90, length = 0.1)

mean(alocoh)
mean(flocoh)
mean(dlocoh)
mean(elocoh)

```

