---
title: "Lab 2 - Build a map"
output: html_notebook
---

Loading in required packages
```{r}
require(tidyverse)
require(sf)
require(tigris)
require(geodata)
require(terra)
require(colorspace)
require(tidyterra)
require(ggnewscale)
require(cowplot)
require(FedData)
require(ggspatial)
```

Load in needed files
```{r}
claibornesf <- st_read("/Volumes/NO NAME/USB Drive/PhD research and documents/Spatial Ecology Class/Labs/Lab 2/Claiborne Shapefile/Claiborne.shp")

receiversf <- st_read("/Volumes/NO NAME/USB Drive/PhD research and documents/Spatial Ecology Class/Labs/Lab 2/Receiver Points/Receiver points.shp")
```

plot shapefiles to make sure they loaded correctly
```{r}
plot(st_geometry(claibornesf))
plot(st_geometry(receiversf))
```

Next, create a bounding box around the study area so it can be plotted on a larger map
```{r}
claiborne = st_bbox(claibornesf)
claiborne

claiborne = claiborne + c(-20000, -20000, 20000, 20000)
claiborne

claiborne = st_as_sfc(claiborne)
plot(claiborne)
```

To create zoomed-out map, bring in shapefile of Alabama and plot bounding box on the shapefile
```{r}
Alabama = states() %>% 
  filter(NAME=='Alabama')

plot(st_geometry(Alabama))

st_crs(Alabama)$proj4string

Alabama = st_transform(Alabama, st_crs(claibornesf))

##overlay map
plot(st_geometry(Alabama))
plot(claiborne, col='red', add=T)
```

Now let's create the zoomed in map
I am going to make a smaller bounding box for this map so that we can more easily see the data 
```{r}
claiborne1 = st_bbox(claibornesf)
claiborne1

claiborne1 = claiborne1 + c(-1000, -1000, 1000, 1000)
claiborne1

claiborne1 = st_as_sfc(claiborne1)
plot(claiborne1)
```

Next, overlay the a raster containing land use from the nlcd in the FedData package on the claiborne spatial file
```{r}
claiborne_nlcd <- get_nlcd(
  template = claiborne1,
  label = "Claiborne",
  year = 2021,
  dataset = "landcover",
  landmass = "L48")

plot(claiborne_nlcd)

```

Before putting everything together, reproject the object that was just created in UTMs
```{r}
claiborne_nlcd = project(claiborne_nlcd, crs(claibornesf, proj=T))
```

Not put everything together with cowplot starting with the zoomed-out map
```{r}
zoomedOut = ggplot()+
  geom_sf(data = Alabama)+
  geom_sf(data = claiborne, fill=NA, color='red')+
  annotation_scale(location="br")+
  annotation_north_arrow(location = "tr")
zoomedOut

zoomedOut = zoomedOut +
  theme_bw()+ #Gets rid of most of the colors
  theme(panel.grid=element_blank(), #Removes the gridlines
        axis.text=element_blank(), #Removes the axis text
        axis.ticks=element_blank(), #Removes the axis tick marks
        panel.border=element_blank()) #Removes the frame around the graph
zoomedOut
```

Build the zoomed in map by overlaying the site shapefile and the receiver locations onto the land cover object
```{r}
zoomedIn = ggplot()+
  geom_spatraster(data = claiborne_nlcd)
zoomedIn

zoomedIn = zoomedIn + 
  new_scale_fill()+
  geom_sf(data=claibornesf, alpha=0.5)
zoomedIn

zoomedIn = zoomedIn + 
  new_scale_fill()+
  geom_sf(data=receiversf, color = 'black')+
  annotation_scale()+
  annotation_north_arrow(location = "br")
zoomedIn

zoomedIn = zoomedIn +
  theme(panel.grid=element_blank(), #Removes the gridlines
        axis.text=element_blank(), #Removes the axis text
        axis.ticks=element_blank(), #Removes the axis tick marks
        panel.border=element_blank()) #Removes the frame around the graph
zoomedIn
```

Combine the zoomed-in and zoomed-out maps onto one figure
```{r}
plot_grid(zoomedOut, zoomedIn)
```

Organize the figure so that it is not messy and looks nice
```{r}
legend = get_legend(zoomedIn)
ggdraw(legend)

zoomedIn1 = zoomedIn + theme(legend.position='none')

supportingFig = plot_grid(zoomedOut, ggdraw(legend), ncol=1, rel_heights = c(0.5, 1))

supportingFig

plot_grid(zoomedIn1, supportingFig, rel_widths=c(1, 0.5))
```

This map represents an array of acoustic telemetry receivers below Claiborne Lock and Dam on the Alabama River. The receiver array will be used to track fish movements below the dam to determine how fish use the area below the dam. The zoomed out map in the upper right corner shows where Claiborne Lock and Dam is located in the state of Alabama. I got the state of Alabama shapefile from the tigris package and overlayed a bounding box around Claiborne Lock and Dam on the Alabama Shapefile. I chouse these spatial elements to show where the study site is in reference to an object everyone is familiar with, the state of Alabama. The zoomed-in map represents the site of this study and surrounding area. The raster is land cover data fron the nlcd in the FedData package. I chose to include landcover data because it shows where the river is in the system and what the surronding floodplain looks like. The shaded polygon represents the open water area below Claiborne Lock and Dam where this study will occur and the black points represent the location of individual acoustic receivers in the array. I chose these spatial elements to visulize the area in which the study will occur and the position of receivers in that study site where the data will be collected.  